---
title: "R markdown template"
author: "Adam Finnemann"
date: "September 24, 2017"
---
Aim: get an complete overview of the specific sections (onames) for LoN workers that worked in sections (as fname).

  
```{r setup, include=FALSE}

library(pacman)
p_load("stringr","ggplot2","ggExtra","lmerTest","tidyverse", "zoo","lubridate", "data.table")

setwd("~/Historie projekt/historie project/LONSEA_DB/fall17/all_nations")


da <- read.csv(list.files(pattern = "reversed"))
```


Section workers is found by searching for "Section" in fname. Workers with fname = "Secretary of Section" are excluded.

```{r}
section_worker <- da %>% 
  filter(str_detect(da$fname, "Section")) %>%  
  filter(fname != "Secretary of Section")

section_worker %>% 
  filter(!duplicated(id)) %>% 
  nrow

```
356 observations from 261 individuals are found

Their specific sections are found
```{r}
section_worker<-droplevels(section_worker)

sections <-summary(section_worker$oname)

sections <- sections %>% as.data.frame() 
sections$oname <- rownames(sections)

sections
```

Further employment analysis is carried out for the following sections:
health, disarmament, mandates, legal, communications and transit, information, economic and financial section (which goes together with the economic relations section and the financial & economic intelligence service), intellectual cooperation and international bureaux section, minorities (which go together with Administrative and Minorities), the social questions and opium traffic, and the political section

First, the three economic sections are united under 1
Same for "Minorities" and "Admin. and Minotories".

```{r}

oname_correct <- section_worker %>% 
  mutate(oname = str_replace_all(oname, "Financial Section & Economic Intelligence Service","Economic and Financial Section"),
        oname = str_replace_all(oname, "Economic Relations Section","Economic and Financial Section"),
        oname = str_replace_all(oname, "Minorities Section", "Administrative and Minorities Section")
         )

```

Workers belonging to large sections are extracted. "large section" is defined as sections with 10 or more contracts.
```{r}


large_section <- summary(section_worker$oname) %>% 
  as.data.frame()
large_section = mutate(large_section,oname = rownames(large_section)) 

large_section <- filter(large_section, . >9)


large_section_worker <- section_worker %>% 
  filter(oname %in% large_section$oname) %>% 
  droplevels(large_section$oname)

summary(large_section_worker$oname)

```
293 contracts remain in the 13 largest sections. 

First gender balance for large sections are found as a table and visualized
```{r}
large_section_worker$gender <- as.factor(large_section_worker$gender)

large_section_worker <- large_section_worker %>% 
  mutate(gender = recode(gender,"0" = "male", "1"="female"))

large_section_worker %>% 
group_by(oname, gender) %>% 
  tally()

```


```{r}
large_section_worker %>% 
   ggplot(aes(gender)) + 
  geom_histogram(stat = "count", aes(fill = gender)) + 
  scale_color_hue()+
  labs(x = "Gender", y = "Count")+
  facet_wrap(~oname)
```

Nationality distribution for the different sections are found:

```{r}
large_section_worker %>% 
group_by(oname, nationality) %>% 
  tally()
```

```{r}
large_section_worker %>% 
   ggplot(aes(nationality)) + 
  geom_histogram(stat = "count", aes(fill = nationality)) + 
  scale_color_hue()+
  labs(x = "Nationality", y = "Count")+
  scale_x_discrete(breaks = NULL)+
  facet_wrap(~oname)
```

nationality analysis

```{r}
source("employment_interval_function.R")

```


Age analysis:
calculating age at contract start and finding average
```{r}
large_section_worker <- large_section_worker %>% 
  mutate(age_at_contract_start = begin_on_year - born_on_year) 
sum(is.na(large_section_worker$age_at_contract_start))
```
There are 68 missing data points for age

In percentage, how many of the contracts from each section are missing the age of the worker:
```{r}
large_section_worker %>% 
  group_by(oname) %>% 
  summarise(NAs = sum(is.na(age_at_contract_start)/length(age_at_contract_start)))
```

What is the average age for of workers at their beggining of their contract:
```{r}
large_section_worker %>% 
  group_by(oname) %>% 
  summarise(mean_age = mean(age_at_contract_start, na.rm = T))




```


```{r}
large_section_worker %>% 
   ggplot(aes(age_at_contract_start)) + 

  geom_histogram(breaks = seq(20,60, 1), aes(fill = ..count..)) + 
  scale_fill_gradient("count", low="orange", high="purple") +
  labs(x = "Age", y = "Count")+
  facet_wrap(~oname)
```


Employment graphs will be made. First a dataframe of contracts with missing data points is made.

```{r}
leftout_contracts <- large_section_worker %>% 
  filter( is.na(large_section_worker$begin_date) | is.na(large_section_worker$end_date))

length(unique(leftout_contracts$pname))

```

21 contract coming from 17 different people have missing data points and won't be in the following analysis. The contract comes from the following sections.
```{r}
summary(droplevels(leftout_contracts$oname))

```

The 21 left out contracts are:
```{r}
leftout_contracts %>% select(pname, oname, begin_date, end_date)
```


```{r}
source("employment_interval_function.R")

plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[1])

employment(plot, title1 = levels(large_section_worker$oname)[1])

```

```{r}

plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[2])

employment(plot, title1 = levels(large_section_worker$oname)[2])

```


```{r}

plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[3])

employment(plot, title1 = levels(large_section_worker$oname)[3])

```
```{r}

plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[4])

employment(plot, title1 = levels(large_section_worker$oname)[4])

```

```{r}

plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[5])

employment(plot, title1 = levels(large_section_worker$oname)[5])

```

```{r}


plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[6])

employment(plot, title1 = levels(large_section_worker$oname)[6])

```

```{r}

plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[7])

employment(plot, title1 = levels(large_section_worker$oname)[7])

```



```{r}

plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[2])

employment(plot, title1 = levels(large_section_worker$oname)[2])

```


```{r}

plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[8])

employment(plot, title1 = levels(large_section_worker$oname)[8])

```



```{r}

plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[9])

employment(plot, title1 = levels(large_section_worker$oname)[9])

```


```{r}


plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[10])

employment(plot, title1 = levels(large_section_worker$oname)[10])

```

```{r}


plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[11])

employment(plot, title1 = levels(large_section_worker$oname)[11])

```

```{r}


plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[12])

employment(plot, title1 = levels(large_section_worker$oname)[12])

```
```{r}


plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[13])

employment(plot, title1 = levels(large_section_worker$oname)[13])

```
