---
title: "Section analysis, number of works"
author: "Adam Finnemann"
date: "September 21, 2017"
output:
  html_document: default
  pdf_document: default
---
Question: 
How many people were there overall in the section over time. This is answered by extracting all observations were "Section" is part of the fname, EXCEPT(!) fname = "Secretary of Section". They are excluded, since they belong to another group


```{r setup, include=FALSE}

list.of.packages <- c("stringr","ggplot2","ggExtra","lmerTest","tidyverse", "zoo","lubridate", "data.table")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages, dependencies = TRUE)
for(i in 1:length(list.of.packages)){
  require(list.of.packages[i], character.only = TRUE)
}

setwd("~/Historie projekt/historie project/LONSEA_DB/fall17/all_nations")



da <- read.csv(list.files(pattern ="rever"))

```

```{r}


section_worker <- da %>% 
  filter(str_detect(da$fname, "Section")) %>%  
  filter(fname != "Secretary of Section")


```


Calculating how many different people there were in the Section.
```{r}
section_worker %>% 
  filter(!duplicated(id)) %>% 
  nrow

```

  

There are a total 356 observations of "Section" in the fname column. These comes from 261 different people.

The distrbution of Section fnames is found (some of these are from the same persons)
```{r}
section_worker <- droplevels(section_worker)

summary(section_worker$fname)
```

Preparations for calculating number of people in section over time
```{r, results= "hide"}

mdl_df <- section_worker %>% 
  select(pname, fname_code,begin_date, end_date) %>% 
  mutate(begin_date = as.Date(begin_date),
         end_date = as.Date(end_date))



setDT(mdl_df)[
  # right join with sequence of monthly intervals
  .(mseq = seq(as.Date("1944-01-01"), length.out = 4L, by = "1 month")), 
  # using non-equi join conditions
  on = .(begin_date <= mseq, end_date >= mseq)][
    # reshape from wide to long format,
    # show rank (concatenate in case of multiple ranks)
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]

result <- setDT(mdl_df)[
  .(mseq = seq(as.Date("1919-01-01"), as.Date("1948-12-30"), by = "1 month")), 
  on = .(begin_date <= mseq, end_date >= mseq), nomatch = 0L, allow.cartesian = TRUE][
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]

```

The above lines creates the time_point/person_contract data_frame. It's visualized below with its three first time points (19-10-01 to 1919-12-01).

It has 245 observations, meaning that 261-245 = 16 people from the section isn't represented.


Here is a list of the 16 not included people. This is due to missing data points.
I'll create a table with all the missing data frames for all the section people in the last part of this document.
```{r}
left_out <- section_worker$pname[!(section_worker$pname %in% result$pname)]
unique(left_out)

```





```{r}
result[1:40,1:3]
```
Number of Section workers for each time period is calculated:
```{r}


removed <- result[,-1]

time_section <- matrix(nrow = (ncol(removed)), ncol = 1)

for (i in 1:(nrow(time_section))){
  time_section[i] = sum(removed[,i, with = F] != "")
}


dates <- as.character(colnames(removed))

plot.df <- cbind(time_section,dates) %>% 
  as.data.frame() %>% 
  mutate(dates = as.Date(dates),
         V1 = as.numeric(as.character(V1))) %>% 
  rename(Section_Workers = V1)


```

The dataframe shown below contains the number of section workers per month for the 250 section members.
```{r}
plot.df
```

The number of people in the section as a bar plot:
```{r}
plot.df %>% 
  ggplot(aes(dates, Section_Workers, color = Section_Workers)) +
  geom_col()+
  labs(x = "Year", y ="Number of Section workers (+1 month)", titles ="Number of people in LoN Section (+1 Month)")+
  scale_x_date(date_breaks = "3 year", date_labels = "%Y")
  


```

Lastly I'll make a list of the section workers that didn't make it into the analysis due to missing dates. 
```{r}
NAs <- filter(section_worker, is.na(section_worker$end_date) | is.na(section_worker$begin_date)) %>% select(pname, fname, begin_on_day, begin_on_month,begin_on_day, end_on_day,end_on_month, end_on_year )



#write.csv(NAs, "Section_workers_missing_data.csv")
NAs
```

