---
title: "R sectio nationality analsysi"
author: "Adam Finnemann"
date: "September 24, 2017"
---

```{r setup, include=FALSE}

library(pacman)
p_load("stringr","ggplot2","ggExtra","lmerTest","tidyverse", "zoo","lubridate", "data.table")



setwd("~/Historie projekt/historie project/LONSEA_DB/fall17/all_nations")

```



Question: How many nationas are there in the League over time:

Reading in list of nationations in the League. Data from wikipedia
```{r}
members <- read.csv("membership_overview.csv", sep = ";", na.strings = c("NA", "")) 

```

creating dataframe of number of members per year
```{r}
per_year <- sapply(members, function(x) sum(!is.na(x))) 

year <- str_replace_all(names(per_year), "X","")

per_year <- data.frame(per_year, year) %>% 
  mutate(year = as.Date(paste0(year, '-01-01')))


per_year
```


plotting number of nations
```{r}

per_year %>% 
  ggplot(aes(year, per_year, color = per_year)) +
  geom_point() +
  geom_line() +
  labs(x = "Year", y = "Nations per year", title = "Nations in the League")

```

Question: How many nations have at lease one person in the Section over time:


```{r}
da <- read.csv(list.files(pattern = "reve"))

section_worker <- da %>% 
  filter(str_detect(da$fname, "Section")) %>%  
  filter(fname != "Secretary of Section")


```

Creating employment df

```{r}
source("employment_interval_function.R")

nat_df <- section_worker %>% 
  mutate(pname = nationality)


mdl_df <- nat_df %>% 
  select(pname, fname_code,begin_date, end_date) %>% 
  mutate(begin_date = as.Date(begin_date),
         end_date = as.Date(end_date))



setDT(mdl_df)[
  # right join with sequence of monthly intervals
  .(mseq = seq(as.Date("1944-01-01"), length.out = 4L, by = "1 month")), 
  # using non-equi join conditions
  on = .(begin_date <= mseq, end_date >= mseq)][
    # reshape from wide to long format,
    # show rank (concatenate in case of multiple ranks)
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]

result <- setDT(mdl_df)[
  .(mseq = seq(as.Date("1919-01-01"), as.Date("1948-12-30"), by = "1 month")), 
  on = .(begin_date <= mseq, end_date >= mseq), nomatch = 0L, allow.cartesian = TRUE][
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]


removed <- result[,-1]

time_section <- matrix(nrow = (ncol(removed)), ncol = 1)

for (i in 1:(nrow(time_section))){
  time_section[i] = sum(removed[,i, with = F] != "")
}


dates <- as.character(colnames(removed))

plot.df <- cbind(time_section,dates) %>% 
  as.data.frame() %>% 
  mutate(dates = as.Date(dates),
         V1 = as.numeric(as.character(V1))) %>% 
  rename(Section_Workers = V1)

plot <- plot.df %>% 
  ggplot(aes(dates, Section_Workers, color = Section_Workers )) +
  geom_col()+
  labs(x = "Year", y ="Nr of countries", titles = "Countries with at least 1 worker")+
  scale_x_date(date_breaks = "3 year", date_labels = "%Y")


plot


```

Plot with nr. of nations in League and nations with Workers in section.
Assumptions:
Nations are represented as being part of the League from januar 1. of the year they joined.
Period visualized is 1920-01-01 to 1947-10-01
Number of workers in section is calculated for each Month
```{r}
per_month = per_year[rep(seq_len(nrow(per_year)), each=12),] 


plot.df <- plot.df[-c(1:6),]
per_month = per_month[1:334,]
plot.df$Nations_in_League <- per_month$per_year 

colnames(plot.df) <- c("Nations_with_worker","Years","Nations_in_league")

long_plot <- gather(plot.df, key, value, Nations_in_league,Nations_with_worker)



long_plot %>% 
  ggplot(aes(x = Years, y = value, color = key)) +
 # geom_point() +
  geom_line() +
  labs(x = "Year", y = "Nations and workers in Section per year", title = "Nations and Workers in Section")+
  scale_x_date(date_labels = "%Y", date_breaks = "3 years")


```

```{r}


mdl_df <- section_worker %>% 
  select(pname, fname_code,begin_date, end_date) %>% 
  mutate(begin_date = as.Date(begin_date),
         end_date = as.Date(end_date))



setDT(mdl_df)[
  # right join with sequence of monthly intervals
  .(mseq = seq(as.Date("1944-01-01"), length.out = 4L, by = "1 month")), 
  # using non-equi join conditions
  on = .(begin_date <= mseq, end_date >= mseq)][
    # reshape from wide to long format,
    # show rank (concatenate in case of multiple ranks)
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]

result <- setDT(mdl_df)[
  .(mseq = seq(as.Date("1919-01-01"), as.Date("1948-12-30"), by = "1 month")), 
  on = .(begin_date <= mseq, end_date >= mseq), nomatch = 0L, allow.cartesian = TRUE][
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]

result_nats <- merge(result, section_worker[,c(8,20)], by = "pname")

result_nats <- result_nats[,-1]
 

#A MIRACLE!!!
nation_workers <- result_nats %>% 
  group_by(nationality) %>% 
  summarise_all(function(x) sum(x != ""))

long_df <- gather(nation_workers, key, value, `1919-07-01`:`1947-10-01`) %>% 
  mutate(key = as.Date(key)) 
  




 long_df %>% 
  filter(value > 8) %>% 
  ggplot(aes(x = key, y = value, fill = nationality)) +
  geom_col() +
  scale_x_date(date_breaks = "3 year", date_labels = "%Y") +
  labs(x = "Year", y ="Workers", titles = "Nations with +10 Workers in Section")
  

```

Running same analysis for Section workers with oname = Information Section.
In the final plot only data points for each country with more than 1 person in the Information Section is kept. 

```{r}
plot <- filter(section_worker,oname == "Information Section")


mdl_df <- plot %>% 
  select(pname, fname_code,begin_date, end_date) %>% 
  mutate(begin_date = as.Date(begin_date),
         end_date = as.Date(end_date))



setDT(mdl_df)[
  # right join with sequence of monthly intervals
  .(mseq = seq(as.Date("1944-01-01"), length.out = 4L, by = "1 month")), 
  # using non-equi join conditions
  on = .(begin_date <= mseq, end_date >= mseq)][
    # reshape from wide to long format,
    # show rank (concatenate in case of multiple ranks)
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]

result <- setDT(mdl_df)[
  .(mseq = seq(as.Date("1919-01-01"), as.Date("1948-12-30"), by = "1 month")), 
  on = .(begin_date <= mseq, end_date >= mseq), nomatch = 0L, allow.cartesian = TRUE][
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]

result_nats <- merge(result, section_worker[,c(8,20)], by = "pname")

result_nats <- result_nats[,-1]
 

#A MIRACLE!!!
nation_workers <- result_nats %>% 
  group_by(nationality) %>% 
  summarise_all(function(x) sum(x != ""))

long_df <- gather(nation_workers, key, value, `1919-09-01`:`1942-12-01`) %>% 
  mutate(key = as.Date(key)) 
  




 long_df %>% 
  filter(value > 1) %>% 
  ggplot(aes(x = key, y = value, fill = nationality)) +
  geom_col() +
  scale_x_date(date_breaks = "3 year", date_labels = "%Y") +
  labs(x = "Year", y ="Workers", titles = "Nations with +10 Workers in Section")
  

employment(plot, title1 = levels(large_section_worker$oname)[1])

```

