---
title: "Analysis of Scandinavians for Torsten"
author: "Adam Finnemann"
date: "Nom, 2017"
---
  

```{r setup, include=FALSE}

library(pacman)
p_load("stringr","ggplot2","ggExtra","lmerTest","tidyverse", "zoo","lubridate", "data.table")

setwd("~/Historie projekt/historie project/LONSEA_DB/fall17/yearly_length_contract_karen")

da <- read.csv(list.files(pattern = "contract_"))
```

Subsetting scandinavians and section workers + directors. The file missing_scandinavians contains the cotracts not included in this analysis. This is total of 4 people, 3 of them are Temporary Collaborators from the Information Section.
Scandinavia is defined as Danes, Swedes and Norwegians.
```{r}

top_scandi <- da %>% 
  filter(nationality %in% c("Dane","Swedish","Norwegian"),
         str_detect(da$fname, "Section") | str_detect(da$fname, "Director"),
         id != "5042", #begin data is before start date.
         fname != "Secretary of Section") %>% 
  droplevels()

```
Distribution of fnames for 23 contracts are:
```{r}
summary(top_scandi$fname)
```
```{r}
unique(top_scandi$pname)
```
There are 18 different people represented.


#1. question: Distribution of work periods.
Defining function and calculating
```{r}
#Function for year/worker employment matrix
employment <- function(df, interval = "1 year"){
  
mdl_df <- df %>% 
  select(pname, fname_code,begin_date, end_date) %>% 
  mutate(begin_date = as.Date(begin_date),
         end_date = as.Date(end_date))



result <- setDT(mdl_df)[
  .(mseq = seq(as.Date("1919-01-01"), as.Date("1948-12-30"), by = interval)), 
  on = .(begin_date <= mseq, end_date >= mseq), nomatch = 0L, allow.cartesian = TRUE][
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]
}

#function for calcualting employment distributions
employment_distribution <- function(df, xseq = seq(0,30,5),yseq = seq(0,2000, 250), group = "people"){ 
result <- employment(df)

contract_length <- matrix(nrow = (nrow(result)), ncol = 1)

result <- as.data.frame(result)

names <- as.character(result[,1])

#removing pname column 
contracts<- sapply(result[,-1],function(x) x != "") %>% 
  rowSums() %>% 
  as.data.frame() %>% 
  dplyr::rename(contract_length = ".") %>% 
  mutate(names = as.factor(names))


contracts %>% 
  ggplot(aes(contract_length, color = contract_length)) +
  geom_histogram(binwidth = 1, aes(fill = ..count..)) +
  scale_fill_gradient("count", low="orange", high="purple") +
  labs(x = "Work periods in years", y = "Number of people", title = paste("Distribution of work periods in LoN for",group)) +
  scale_x_continuous(breaks = xseq)+
  scale_y_continuous(breaks = yseq)
}
```

For each scandinavian, how many years in LoN:
```{r}
employment_distribution(top_scandi, group = "Scandinavians", yseq = seq(0,5,1))
```
Work periods are calcualted inclusively. The 25 year work period is from 1921 to 1946.


Repeating analysis, only including the first contract for each person
```{r}
top_scandi %>% 
  filter(!duplicated(pname)) %>% 
  employment_distribution( group = "Scandinavians", yseq = seq(0,5,1))
```



#Second measure of "lenght of contract"

For each year, how long does contracts from that year last - including all contracts
```{r}
top_scandi <-top_scandi  %>% 
  mutate(end_date = as.Date(end_date),
         begin_date = as.Date(begin_date),
         duration = end_date - begin_date, 
         duration = as.numeric(duration))

contract_length_per_year <- top_scandi %>% 
  mutate(begin_date = as.factor(begin_date)) %>% 
  group_by(begin_date) %>% 
  dplyr::summarise(mean = mean(duration))



contract_length_per_year %>% 
  mutate(begin_date = as.Date(begin_date),
         mean = as.numeric(mean)) %>% 
  ggplot(aes(begin_date,mean, color = mean)) +
  geom_point() +
  geom_smooth(se = F) +
  labs(x = "Year", y ="Days of contract", titles = "Average length of contract in years for top Scandinavians")+
  scale_x_date(date_breaks = "3 year", date_labels = "%Y")+
  scale_y_continuous(breaks =seq(0, 30*365, 365),labels = paste(1:length(seq(0, 30*365, 365)), "years"))


```
The line summarising the trend can be change to a straight line if that's better.
The plots includes all top Scandinavian contracts (not just each person's first contract).


#2. Distribution of work periods for Scandinavians in first division


Subsetting scandinavians in first division
```{r}
firstd_scandi <- da %>% 
  filter(nationality %in% c("Dane","Swedish","Norwegian"),
         canonical_fname == "First Division",
         id != "5042") %>%  #begin data is before start date.
  droplevels()
```
There are 66 contracts in first division from Scandinavians


```{r}
unique(firstd_scandi$pname)
```
There are 57 different Scandinavians represented in the first division

Calculating employment intervals
```{r}
employment_distribution(firstd_scandi,xseq = seq(0,30,1), yseq = seq(0,5,1), group = levels(top_scandi$oname)[5])
```



#Political vs techincals section analysis

Group 1: Social Questions and Opium Traffic Section; Health Section; Communications and Transit Section; Economic and Financial Section; Intellectual Cooperation and International Bureaux Section.


```{r}
filter(top_scandi, oname %in% c("Social Questions and Opium Traffic Section", "Health Section", "Communications and Transit Section", "Economic and Financial Section", "Intellectual Cooperation and International Bureaux Section")) %>% 
  select(-X.1, -X,-id)

```
There are 7 people represented

Visualizing length of contracts
```{r}
filter(top_scandi, oname %in% c("Social Questions and Opium Traffic Section", "Health Section", "Communications and Transit Section", "Economic and Financial Section", "Intellectual Cooperation and International Bureaux Section")) %>% 
  employment_distribution(xseq = seq(0,30,1), yseq = seq(0,5,1), group = levels(top_scandi$oname)[5])

```

Group 3: Political Section; Information Section; Legal Section; Disarmament Section.  
```{r}
filter(top_scandi, oname %in% c("Political Section", "Information Section", "Legal Section", "Disarmament Section" )) %>% 
  select(-X.1, X, -gender)

```
4 People are represented in the second group

calculating distribution of length of contracts

```{r}
filter(top_scandi, oname %in% c("Political Section", "Information Section", "Legal Section", "Disarmament Section" )) %>% 
employment_distribution(xseq = seq(0,30,1), yseq = seq(0,5,1), group = levels(top_scandi$oname)[5])
```


#Breaking down graphs into sections

```{r}
summary(top_scandi$oname)
```

Calculating mean length of each contract for each section. This is shown in a table, since I think it's easier to compare than lots of graphs with few bars

```{r}
knitr::opts_chunk$set(rows.print=40)

top_scandi %>% 
   mutate(end_date = as.Date(end_date),
          being_date = as.Date(begin_date),
          duration = difftime(end_date, begin_date, units = "days")) %>% 
  select(pname, oname, duration) 



```




Plotting the distribution of work periods for the sections with more than 2 contracts.
```{r}
employment_distribution(filter(top_scandi, oname == levels(oname)[1]),xseq = seq(0,30,1), yseq = seq(0,5,1), group = levels(top_scandi$oname)[1])
```
```{r}
employment_distribution(filter(top_scandi, oname == levels(oname)[5]),xseq = seq(0,30,1), yseq = seq(0,5,1), group = levels(top_scandi$oname)[5])
```






