---
title: "R section nationality analysis"
author: "Adam Finnemann"
date: "Jan 30, 2017"
---
  
#Assumptions:
All british and English people are united under the name of "British".
All months and days are set to 01, thus a person needs to be in the Secretariat for at least 1 day in a year to be counted in. 
Higher officials are defined as, members of section, directors, chiefs, experts, heads. Only "heads of" are included, this exlcudes head driver and head cleaner.
Contracts with unknown nationality are excluded.
```{r setup}

library(pacman)
p_load("stringr","ggplot2","ggExtra","lmerTest","tidyverse", "zoo","lubridate", "data.table")

setwd("~/Historie projekt/historie project/LONSEA_DB/spring18/proportion_of_scandis")

da <- read.csv("contract_length_w_begin_year.csv")

higher_officials <- da %>% 
  filter(str_detect(da$fname, "Section")| #including "Section"
         str_detect(da$fname, "Director")| #Including Directors
         str_detect(da$fname, "Chief") | #Including Chief
         str_detect(da$fname, "Expert")|
         str_detect(da$fname, "Head of"), #Including Expert
         fname != "Secretary of Section") %>% 
  #filter(canonical_fname != "First Division" & str_detect(da$fname, "Head") %>% 
  droplevels()

higher_officials <- higher_officials %>% 
  filter(nationality != "") %>% 
  mutate(nationality = recode(nationality, "English" = "British"))

unknown = da %>% 
  filter(nationality == "")
```


An overview of the fnames found among higher officials. Acting directors are included. There is a Chief Librarian in there?
```{r}
summary(higher_officials$fname)
```



forming nationality/employment data frame
```{r}


mdl_df <- higher_officials %>% 
  select(pname, fname_code,begin_date, end_date) %>% 
  mutate(begin_date = as.Date(begin_date),
         end_date = as.Date(end_date))

result <- setDT(mdl_df)[
  .(mseq = seq(as.Date("1919-01-01"), as.Date("1948-12-30"), by = "1 year")), 
  on = .(begin_date <= mseq, end_date >= mseq), nomatch = 0L, allow.cartesian = TRUE][
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]

result_nats <- left_join(result, select(higher_officials, pname, nationality)) %>% 
  filter(!duplicated(.))

result_nats_wo_pname <- result_nats[,-1]
 


nation_workers <- result_nats_wo_pname %>% 
  group_by(nationality) %>% 
  summarise_all(function(x) sum(x != ""))

long_df <- gather(nation_workers, key, value, `1919-01-01`:`1947-01-01`) %>% 
  mutate(key = as.Date(key)) 
  




#function for plotting

plot_section_workers <- function(df, minimum_worker = 5){
df %>% 
  filter(value > minimum_worker) %>% 
  ggplot(aes(x = key, y = value, fill = nationality, color = nationality)) +
  geom_col() +
  scale_x_date(date_breaks = "2 year", date_labels = "%Y") +
  labs(x = "Year", y ="Workers", titles = paste("Nations with", minimum_worker,"+ Workers in Section"))
}


```




```{r}
plot_section_workers(long_df, 15)

```

```{r}
plot_section_workers(long_df, 10)

```

```{r}
plot_section_workers(long_df, 7)

```

```{r}
plot_section_workers(long_df, 6)

```
```{r}
plot_section_workers(long_df, 5)

```

```{r}
plot_section_workers(long_df, 4)

```
```{r}
plot_section_workers(long_df, 3)
```
```{r}
plot_section_workers(long_df, 2)

```

```{r}
plot_section_workers(long_df, 1)
                     

```

