---
title: "R witin section nationality analysis"
author: "Adam Finnemann"
date: "Feb. 2, 2017"
---
  

```{r setup}

library(pacman)
p_load("stringr","ggplot2","ggExtra","lmerTest","tidyverse", "zoo","lubridate", "data.table")

setwd("~/Historie projekt/historie project/LONSEA_DB/spring18/proportion_of_scandis")

da <- read.csv("contract_length_w_begin_year.csv")

higher_officials <- da %>% 
  filter(str_detect(da$fname, "Section")| #including "Section"
           str_detect(da$fname, "Director")| #Including Directors
           str_detect(da$fname, "Chief") | #Including Chief
           str_detect(da$fname, "Expert")|
           str_detect(da$fname, "Head of"), #Including Expert
         fname != "Secretary of Section") %>% 
  #filter(canonical_fname != "First Division" & str_detect(da$fname, "Head") %>% 
  droplevels()

higher_officials <- higher_officials %>% 
  filter(nationality != "") %>% 
  mutate(nationality = recode(nationality, "English" = "British"))

unknown = da %>% 
  filter(nationality == "")
```

Further employment analysis is carried out for the following sections:
health, disarmament, mandates, legal, communications and transit, information, economic and financial section (which is united with "the economic relations section" and "the financial & economic intelligence service"), intellectual cooperation and international bureaux section, minorities (which is united with "Administrative and Minorities"), the social questions and opium traffic, and the political section

```{r}

oname_correct <- higher_officials %>% 
  dplyr::mutate(oname = str_replace_all(oname, "Financial Section & Economic Intelligence Service","Economic and Financial Section"),
                oname = str_replace_all(oname, "Economic Relations Section","Economic and Financial Section"),
                oname = str_replace_all(oname, "Administrative and Minorities Section","Minorities Section"),
                oname = as.factor(oname)) %>% 
  filter(oname != "Treasury") %>% 
  droplevels



summary(oname_correct$oname)
```



Workers belonging to large sections are extracted. "large section" is defined as sections with 10 or more contracts.
```{r}


large_section <- summary(oname_correct$oname) %>% 
  as.data.frame()

large_section = mutate(large_section,oname = rownames(large_section)) 

large_section <- filter(large_section, . >9)


large_section_worker <- oname_correct %>% 
  filter(oname %in% large_section$oname) %>% 
  droplevels(large_section$oname)

summary(large_section_worker$oname)

```

Defnining function for visualizing workers per year in sections


```{r}

library(pacman)
p_load("stringr","ggplot2","ggExtra","lmerTest","tidyverse", "zoo","lubridate", "data.table")

employment <- function(df, interval = "1 year", y_axis = "# of higher officials", x_axis = "Year", title1 = "LoN Workers", minimum_worker = 0) {
  
mdl_df <- df %>% 
  select(pname, fname_code,begin_date, end_date) %>% 
  mutate(begin_date = as.Date(begin_date),
         end_date = as.Date(end_date))



result <- setDT(mdl_df)[
  .(mseq = seq(as.Date("1919-01-01"), as.Date("1948-12-30"), by = interval)), 
  on = .(begin_date <= mseq, end_date >= mseq), nomatch = 0L, allow.cartesian = TRUE][
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]


result_nats <- left_join(result, select(df, pname, nationality)) %>% 
  filter(!duplicated(.))

result_nats_wo_pname <- result_nats[,-1]
 


nation_workers <- result_nats_wo_pname %>% 
  group_by(nationality) %>% 
  summarise_all(function(x) sum(x != ""))

long_df <- gather(nation_workers, key, value, colnames(result_nats)[2]:tail(colnames(result_nats),2)[1]) %>% 
  mutate(key = as.Date(key))  

long_df %>% 
  filter(value > minimum_worker) %>% 
  ggplot(aes(x = key, y = value, fill = nationality, color = nationality)) +
  geom_col() +
  scale_x_date(date_breaks = "2 year", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(0,50,2)) +
  labs(x = x_axis, y =y_axis, titles = paste("Nationalities of the", title1)) -> plot


return(plot)
}

```

```{r}
plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[1])

employment(plot, title1 = levels(large_section_worker$oname)[1])

```


```{r}
plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[2])

employment(plot, title1 = levels(large_section_worker$oname)[2])

```




```{r}
plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[3])

employment(plot, title1 = levels(large_section_worker$oname)[3])

```


```{r}
plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[4])

employment(plot, title1 = levels(large_section_worker$oname)[4])

```


```{r}
employment(plot,minimum_worker = 1, title1 = levels(large_section_worker$oname)[4])

```


```{r}
plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[5])

employment(plot, title1 = levels(large_section_worker$oname)[5])

```


```{r}
employment(plot, minimum_worker = 1, title1 = levels(large_section_worker$oname)[5])
```


```{r}
plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[6])

employment(plot, title1 = levels(large_section_worker$oname)[6])

```

```{r}
employment(plot, minimum_worker = 1, title1 = levels(large_section_worker$oname)[6])

```



```{r}
plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[7])

employment(plot, title1 = levels(large_section_worker$oname)[7])

```


```{r}
plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[8])

employment(plot, title1 = levels(large_section_worker$oname)[8])

```





```{r}
plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[9])

employment(plot, title1 = levels(large_section_worker$oname)[9])

```


```{r}
plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[10])

employment(plot, title1 = levels(large_section_worker$oname)[10])

```


```{r}
plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[11])

employment(plot, title1 = levels(large_section_worker$oname)[11])

```


```{r}
plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[12])

employment(plot, title1 = levels(large_section_worker$oname)[12])

```



## Scandi vs rest for Minorities, Mandates and Economics. 


```{r}

scandi_rest = large_section_worker %>% 
  mutate(nationality = ifelse(nationality %in% c("Swedish","Dane","Norwegian"),"Scandinavian","Non_Scandinavian"))
```

```{r}
employment2 <- function(df, interval = "1 year", y_axis = "# of higher officials", x_axis = "Year", title1 = "LoN Workers", minimum_worker = 0, max_y = 50) {
  
mdl_df <- df %>% 
  select(pname, fname_code,begin_date, end_date) %>% 
  mutate(begin_date = as.Date(begin_date),
         end_date = as.Date(end_date))



result <- setDT(mdl_df)[
  .(mseq = seq(as.Date("1919-01-01"), as.Date("1948-12-30"), by = interval)), 
  on = .(begin_date <= mseq, end_date >= mseq), nomatch = 0L, allow.cartesian = TRUE][
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]


result_nats <- left_join(result, select(df, pname, nationality)) %>% 
  filter(!duplicated(.))

result_nats_wo_pname <- result_nats[,-1]
 


nation_workers <- result_nats_wo_pname %>% 
  group_by(nationality) %>% 
  summarise_all(function(x) sum(x != ""))

long_df <- gather(nation_workers, key, value, colnames(result_nats)[2]:tail(colnames(result_nats),2)[1]) %>% 
  mutate(key = as.Date(key))  

long_df %>% 
  filter(value > minimum_worker) %>% 
  ggplot(aes(x = key, y = value, fill = nationality, color = nationality)) +
  geom_point() +
  geom_line()+
  scale_x_date(date_breaks = "2 year", date_labels = "%Y") +
  scale_y_continuous(limits = c(0,max_y),breaks = seq(0,max_y,2))  +
  labs(x = x_axis, y =y_axis, titles = paste("Nationalities of the", title1)) -> plot


return(plot)
}


```

```{r}
plot <- filter(scandi_rest,oname == levels(scandi_rest$oname)[4])

employment2(plot, title1 = levels(large_section_worker$oname)[4],max_y = 30)

```

```{r}
plot <- filter(scandi_rest,oname == levels(scandi_rest$oname)[9])

employment2(plot, title1 = levels(large_section_worker$oname)[9], max_y = 5)

```


```{r}
plot <- filter(scandi_rest,oname == levels(scandi_rest$oname)[10])

employment2(plot, title1 = levels(large_section_worker$oname)[10], max_y = 8)

```

```{r}

```


##Plotting both directors and all.



```{r}
employment3 <- function(df, interval = "1 year", y_axis = "# of higher officials", x_axis = "Year", title1 = "LoN Workers", minimum_worker = 0, max_y = 50) {
  
mdl_df <- df %>% 
  select(pname, fname_code,begin_date, end_date) %>% 
  mutate(begin_date = as.Date(begin_date),
         end_date = as.Date(end_date))



result <- setDT(mdl_df)[
  .(mseq = seq(as.Date("1919-01-01"), as.Date("1948-12-30"), by = interval)), 
  on = .(begin_date <= mseq, end_date >= mseq), nomatch = 0L, allow.cartesian = TRUE][
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]


result_nats <- left_join(result, select(df, pname, nationality)) %>% 
  filter(!duplicated(.))

result_nats_wo_pname <- result_nats[,-1]
 


nation_workers <- result_nats_wo_pname %>% 
  group_by(nationality) %>% 
  summarise_all(function(x) sum(x != ""))

long_df <- gather(nation_workers, key, value, colnames(result_nats)[2]:tail(colnames(result_nats),2)[1]) %>% 
  mutate(key = as.Date(key),
         group = "all")

#repeating for directors only
mdl_df2 <- df %>% 
  filter(fname == "Director") %>% 
  select(pname, fname_code,begin_date, end_date) %>% 
  mutate(begin_date = as.Date(begin_date),
         end_date = as.Date(end_date))
if(nrow(mdl_df2) == 0){
  print("no directors")}


result2 <- setDT(mdl_df2)[
  .(mseq = seq(as.Date("1919-01-01"), as.Date("1948-12-30"), by = interval)), 
  on = .(begin_date <= mseq, end_date >= mseq), nomatch = 0L, allow.cartesian = TRUE][
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]


result_nats2 <- left_join(result2, select(df, pname, nationality)) %>% 
  filter(!duplicated(.))

result_nats_wo_pname2 <- result_nats2[,-1]
 


nation_workers2 <- result_nats_wo_pname2 %>% 
  group_by(nationality) %>% 
  summarise_all(function(x) sum(x != ""))

long_df2 <- gather(nation_workers2, key, value, colnames(result_nats2)[2]:tail(colnames(result_nats2),2)[1]) %>%
  mutate(key = as.Date(key),
         group = "directors")  

long_df3 = rbind(long_df2,long_df)

long_df3 %>% 
  filter(value > minimum_worker) %>% 
  ggplot(aes(x = key, y = value, fill = nationality, color = nationality)) +
  geom_col() +
  scale_x_date(date_breaks = "2 year", date_labels = "%Y") +
  scale_y_continuous(limits = c(0,max_y),breaks = seq(0,max_y,2))  +
  labs(x = x_axis, y =y_axis, titles = paste("Nationalities of the", title1))+
  facet_grid(group~.)-> plot

return(plot)
}

```

```{r}
plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[1])

employment3(plot, title1 = levels(large_section_worker$oname)[1], max_y = 10)
```
```{r}
plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[2])

employment3(plot, title1 = levels(large_section_worker$oname)[2], max_y = 8)
```
```{r}
#plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[3])

#employment3(plot, title1 = levels(large_section_worker$oname)[3], max_y = 15)
```
No directors

```{r}
plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[4])

employment3(plot, title1 = levels(large_section_worker$oname)[4], max_y = 30)
```
```{r}
plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[5])

employment3(plot, title1 = levels(large_section_worker$oname)[5], max_y = 25)
```
```{r}
plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[6])

employment3(plot, title1 = levels(large_section_worker$oname)[6], max_y = 30)
```
```{r}
#plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[7])

#employment3(plot, title1 = levels(large_section_worker$oname)[7], max_y = 15)
```
No directors

```{r}
plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[8])

employment3(plot, title1 = levels(large_section_worker$oname)[8], max_y = 12)
```
```{r}
plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[9])

employment3(plot, title1 = levels(large_section_worker$oname)[9], max_y = 6)
```
```{r}
plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[10])

employment3(plot, title1 = levels(large_section_worker$oname)[10], max_y = 12)
```


```{r}
plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[11])

employment3(plot, title1 = levels(large_section_worker$oname)[11], max_y = 15)
```
```{r}
#plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[12])

#employment3(plot, title1 = levels(large_section_worker$oname)[12], max_y = 15)
```
no directors
