---
title: "R witin section nationality analysis"
author: "Adam Finnemann"
date: "Feb. 2, 2017"
---
  

```{r setup}

library(pacman)
p_load("stringr","ggplot2","ggExtra","lmerTest","tidyverse", "zoo","lubridate", "data.table")

setwd("~/Historie projekt/historie project/LONSEA_DB/spring18/proportion_of_scandis")

da <- read.csv("contract_length_w_begin_year.csv")

higher_officials2 <- da %>% 
  filter(str_detect(fname, "Section")| #including "Section"
           str_detect(fname, "Director")| #Including Directors
           str_detect(fname, "Chief") | #Including Chief
           str_detect(fname, "Expert")|
           str_detect(fname, "Head of") |
           str_detect(fname, "Section"),
         fname != "Secretary of Section",
         oname != "Treasury",
         oname != "Library",
         oname != "Labour Section",
         canonical_fname != "Second Division") %>% 
  #filter(canonical_fname != "First Division" & str_detect(da$fname, "Head") %>% 
  droplevels()
  

higher_officials <- higher_officials2 %>% 
  filter(nationality != "") %>% 
  mutate(nationality = recode(nationality, "English" = "British"))

unknown = higher_officials2 %>% 
  filter(nationality == "")
```

Further employment analysis is carried out for the following sections:
health, disarmament, mandates, legal, communications and transit, information, economic and financial section (which is united with "the economic relations section" and "the financial & economic intelligence service"), intellectual cooperation and international bureaux section, minorities (which is united with "Administrative and Minorities"), the social questions and opium traffic, and the political section

```{r}

oname_correct <- higher_officials %>% 
  dplyr::mutate(oname = str_replace_all(oname, "Financial Section & Economic Intelligence Service","Economic and Financial Section"),
                oname = str_replace_all(oname, "Economic Relations Section","Economic and Financial Section"),
                oname = str_replace_all(oname, "Administrative and Minorities Section","Minorities Section"),
                oname = as.factor(oname)) %>% 
  filter(oname != "Treasury", oname != "Library") %>% 
  droplevels



#summary(oname_correct$oname)
```



Workers belonging to large sections are extracted. "large section" is defined as sections with 10 or more contracts.
```{r}


large_section <- summary(oname_correct$oname) %>% 
  as.data.frame()

large_section = mutate(large_section,oname = rownames(large_section)) 

large_section <- filter(large_section, . >9)


large_section_worker <- oname_correct %>% 
  filter(oname %in% large_section$oname) %>% 
  droplevels(large_section$oname)

#summary(large_section_worker$oname)

```

Defnining function for visualizing workers per year in sections


```{r}

library(pacman)
p_load("stringr","ggplot2","ggExtra","lmerTest","tidyverse", "zoo","lubridate", "data.table")

employment <- function(df, interval = "1 year", y_axis = "# of higher officials", x_axis = "Year", title1 = "LoN Workers", minimum_worker = 0) {
  
mdl_df <- df %>% 
  select(pname, fname_code,begin_date, end_date) %>% 
  mutate(begin_date = as.Date(begin_date),
         end_date = as.Date(end_date))



result <- setDT(mdl_df)[
  .(mseq = seq(as.Date("1919-01-01"), as.Date("1948-12-30"), by = interval)), 
  on = .(begin_date <= mseq, end_date >= mseq), nomatch = 0L, allow.cartesian = TRUE][
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]


result_nats <- left_join(result, select(df, pname, nationality)) %>% 
  filter(!duplicated(.))

result_nats_wo_pname <- result_nats[,-1]
 


nation_workers <- result_nats_wo_pname %>% 
  group_by(nationality) %>% 
  summarise_all(function(x) sum(x != ""))

long_df <- gather(nation_workers, key, value, colnames(result_nats)[2]:tail(colnames(result_nats),2)[1]) %>% 
  mutate(key = as.Date(key))  

long_df %>% 
  filter(value > minimum_worker) %>% 
  ggplot(aes(x = key, y = value, fill = nationality, color = nationality)) +
  geom_col() +
  scale_x_date(date_breaks = "2 year", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(0,50,2)) +
  labs(x = x_axis, y =y_axis, titles = paste("Nationalities of the", title1)) -> plot


return(plot)
}

```

```{r}
#plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[1])

#employment(plot, title1 = levels(large_section_worker$oname)[1])

```


```{r}
#plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[2])

#employment(plot, title1 = levels(large_section_worker$oname)[2])

```




```{r}
#plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[3])

#employment(plot, title1 = levels(large_section_worker$oname)[3])

```


```{r}
#plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[4])

#employment(plot, title1 = levels(large_section_worker$oname)[4])

```


```{r}
#employment(plot,minimum_worker = 1, title1 = levels(large_section_worker$oname)[4])

```


```{r}
#plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[5])

#employment(plot, title1 = levels(large_section_worker$oname)[5])

```


```{r}
#employment(plot, minimum_worker = 1, title1 = levels(large_section_worker$oname)[5])
```


```{r}
#plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[6])

#employment(plot, title1 = levels(large_section_worker$oname)[6])

```

```{r}
#employment(plot, minimum_worker = 1, title1 = levels(large_section_worker$oname)[6])

```



```{r}
#plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[7])

#employment(plot, title1 = levels(large_section_worker$oname)[7])

```


```{r}
#plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[8])

#employment(plot, title1 = levels(large_section_worker$oname)[8])

```





```{r}
#plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[9])

#employment(plot, title1 = levels(large_section_worker$oname)[9])

```
Plot function special for minorities section which is used in article

```{r}
employment <- function(df, interval = "1 year", y_axis = "# of higher officials", x_axis = "Year", title1 = "LoN Workers", minimum_worker = 0, colors ) {
  
mdl_df <- df %>% 
  select(pname, fname_code,begin_date, end_date) %>% 
  mutate(begin_date = as.Date(begin_date),
         end_date = as.Date(end_date))



result <- setDT(mdl_df)[
  .(mseq = seq(as.Date("1919-01-01"), as.Date("1948-12-30"), by = interval)), 
  on = .(begin_date <= mseq, end_date >= mseq), nomatch = 0L, allow.cartesian = TRUE][
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]


result_nats <- left_join(result, select(df, pname, nationality)) %>% 
  filter(!duplicated(.))

result_nats_wo_pname <- result_nats[,-1]
 


nation_workers <- result_nats_wo_pname %>% 
  group_by(nationality) %>% 
  summarise_all(function(x) sum(x != ""))

# nation_workers_wo = nation_workers[,2:30]
# 
# nation_workers_wo %>% 
#   summarise_all(function(x) sum(x)) -> workers_per_year
# 
# n2 = nation_workers
# 
# for (col in 2:30){
#   for (row in 1:49){
#   
#   n2[row,col] = nation_workers[row,col] / workers_per_year[col-1]
#   }
# }
# 
# 



long_df <- gather(nation_workers, key, value, colnames(result_nats)[2]:tail(colnames(result_nats),2)[1]) %>% 
  mutate(key = as.Date(key))  

long_df %>% 
  filter(value > minimum_worker) %>% 
  ggplot(aes(x = key, y = value, fill = nationality, color = nationality)) +
  geom_col() +
  scale_x_date(date_breaks = "2 year", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(0,50,2)) +
  labs(x = x_axis, y =y_axis, titles = title1) +
  theme(legend.title=element_blank())+
  theme(plot.title = element_text(size=11)) + #remove for certain plots
  scale_fill_manual(values= colors) +
  scale_color_manual(values=colors) -> plot


return(plot)
}
```


```{r}

employment_constant <- function(df, interval = "1 year", y_axis = "# of higher officials", x_axis = "Year", title1 = "LoN Workers", minimum_worker = 0, colors ) {
  
mdl_df <- df %>% 
  select(pname, fname_code,begin_date, end_date) %>% 
  mutate(begin_date = as.Date(begin_date),
         end_date = as.Date(end_date))



result <- setDT(mdl_df)[
  .(mseq = seq(as.Date("1919-01-01"), as.Date("1948-12-30"), by = interval)), 
  on = .(begin_date <= mseq, end_date >= mseq), nomatch = 0L, allow.cartesian = TRUE][
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]


result_nats <- left_join(result, select(df, pname, nationality)) %>% 
  filter(!duplicated(.))

result_nats_wo_pname <- result_nats[,-1]
 


nation_workers <- result_nats_wo_pname %>% 
  group_by(nationality) %>% 
  summarise_all(function(x) sum(x != ""))

nation_workers_wo = nation_workers[,2:length(nation_workers)]

nation_workers_wo %>% 
  summarise_all(function(x) sum(x)) -> workers_per_year

n2 = nation_workers

for (col in 2:ncol(n2)){
  for (row in 1:nrow(n2)){
  
  n2[row,col] = nation_workers[row,col] / workers_per_year[col-1]
  }
}





long_df <- gather(n2, key, value, colnames(result_nats)[2]:tail(colnames(result_nats),2)[1]) %>% 
  mutate(key = as.Date(key))  

long_df %>% 
  filter(value > minimum_worker) %>% 
  ggplot(aes(x = key, y = value, fill = nationality, color = nationality)) +
  geom_col() +
  scale_x_date(date_breaks = "2 year", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(0,50,2)) +
  labs(x = x_axis, y =y_axis, titles = title1) +
  theme(legend.title=element_blank())+
  theme(plot.title = element_text(size=11)) + #remove for certain plots
  scale_fill_manual(values= colors) +
  scale_color_manual(values=colors) -> plot


return(plot)
}


#colors = c("dark blue","tomato1","green","bisque","purple","yellow","dark red","light ##blue","orange","black","turquoise","darkmagenta","brown","indianred2","steelblue","yellowgreen")

colors = c("#7f3b08",
"#b35806",
"#e08214",
"#fdb863",
"#fee0b6",
"#949494",
"#5e77c4",
"#b2abd2",
"#8073ac",
"#542788",
"#2d004b",
"#81179c",
"#d3326c",
"#f61c44",
"#d85431",
"#fb6a4a",
"#ef3b2c",
"#cb181d",
"#a50f15",
"#67000d")

plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[11])



employment_constant(plot, title1 = "Members of Section and Directors of all nationalities in the Political Section", colors = colors)


```


```{r}
employment(plot, title1 = "Members of Section and Directors of all nationalities in the Political Section", colors = colors)
```


```{r}
plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[10])

#colors = c("dark blue","tomato1","bisque","green","purple","yellow","dark red","orange","light #blue","black","turquoise","darkmagenta","indianred2","brown","steelblue","yellowgreen", "black")


employment(plot, colors = colors, title1 = "Members of Section and Directors of all nationalities in the Minorities Section")

```




```{r}
plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[4])

colors = c("dark blue","tomato1","brown","green","bisque","purple","orange","steelblue","light blue","black","turquoise","darkmagenta","indianred2","brown","steelblue","yellowgreen")

employment(plot, title1 = "Members of Section and Directors of all nationalities in the Economic and Financial Sections", colors = colors, minimum_worker = 1)
  

```




```{r}
#plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[12])

#employment(plot, title1 = levels(large_section_worker$oname)[12])

```



## Scandi vs rest for Minorities, Mandates and Economics. 


```{r}

scandi_rest = large_section_worker %>% 
  mutate(nationality = ifelse(nationality %in% c("Swedish","Dane","Norwegian"),"Scandinavian","Non_Scandinavian"))
```

```{r}
employment2 <- function(df, interval = "1 year", y_axis = "# of higher officials", x_axis = "Year", title1 = "LoN Workers", minimum_worker = 0, max_y = 50) {
  
mdl_df <- df %>% 
  select(pname, fname_code,begin_date, end_date) %>% 
  mutate(begin_date = as.Date(begin_date),
         end_date = as.Date(end_date))



result <- setDT(mdl_df)[
  .(mseq = seq(as.Date("1919-01-01"), as.Date("1948-12-30"), by = interval)), 
  on = .(begin_date <= mseq, end_date >= mseq), nomatch = 0L, allow.cartesian = TRUE][
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]


result_nats <- left_join(result, select(df, pname, nationality)) %>% 
  filter(!duplicated(.))

result_nats_wo_pname <- result_nats[,-1]
 


#nation_workers <- result_nats_wo_pname %>% 
#  group_by(nationality) %>% 
#  summarise_all(function(x) sum(x != ""))

scandi1 <- result_nats_wo_pname %>% 
  filter(nationality  == "Scandinavian") %>% 
  summarise_all(function(x) sum(x != ""))

all_and_scandi <- result_nats_wo_pname %>% 
  summarise_all(function(x) sum(x != "")) %>% 
  rbind(scandi1) %>% 
  mutate(nationality = ifelse(nationality == 6, "Scandinavian","Total"))


long_df <- gather(all_and_scandi, key, value, colnames(result_nats)[2]:tail(colnames(result_nats),2)[1]) %>% 
  mutate(key = as.Date(key))  

long_df %>% 
  filter(value > minimum_worker) -> long_df
  
#ggplot(aes(x = key, y = value, fill = nationality, color = nationality)) +
ggplot()+
  geom_col(data = filter(long_df, nationality == "Total"), aes(x = key, y = value), fill = "blue") +
  geom_point(data = filter(long_df, nationality == "Scandinavian"), aes(x = key, y = value), color = "red") +
  geom_line(data = filter(long_df, nationality == "Scandinavian"), aes(x = key, y = value), color = "red") +
  scale_x_date(date_breaks = "2 year", date_labels = "%Y") +
  scale_y_continuous(limits = c(0,max_y),breaks = seq(0,max_y,1))  +
  labs(x = x_axis, y =y_axis, titles = paste("Scandinavians vs. other national Members and Directors of the Minorities Section")) -> plot


return(plot)
}


```



```{r}
plot <- filter(scandi_rest,oname == levels(scandi_rest$oname)[10])

employment2(df = plot, title1 = "Scandinavians vs. all other national Members and Directors of the Minorities Section", max_y = 10)

```

```{r}
#plot <- filter(scandi_rest,oname == levels(scandi_rest$oname)[4])

#employment2(plot, title1 = levels(large_section_worker$oname)[4],max_y = 30)

```

```{r}
#plot <- filter(scandi_rest,oname == levels(scandi_rest$oname)[9])

#employment2(plot, title1 = levels(large_section_worker$oname)[9], max_y = 5)

```


##Plotting both directors and all.



```{r}
employment3 <- function(df, interval = "1 year", y_axis = "# of higher officials", x_axis = "Year", title1 = "LoN Workers", minimum_worker = 0, max_y = 50) {
  
  
#mdl df without directors and chiefs of sections
mdl_df <- df %>% 
  filter(fname != "Director" & fname != "Chief of Section") %>% 
  select(pname, fname_code,begin_date, end_date) %>% 
  mutate(begin_date = as.Date(begin_date),
         end_date = as.Date(end_date))



result <- setDT(mdl_df)[
  .(mseq = seq(as.Date("1919-01-01"), as.Date("1948-12-30"), by = interval)), 
  on = .(begin_date <= mseq, end_date >= mseq), nomatch = 0L, allow.cartesian = TRUE][
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]


result_nats <- left_join(result, select(df, pname, nationality)) %>% 
  filter(!duplicated(.))

result_nats_wo_pname <- result_nats[,-1]
 


nation_workers <- result_nats_wo_pname %>% 
  group_by(nationality) %>% 
  summarise_all(function(x) sum(x != ""))

long_df <- gather(nation_workers, key, value, colnames(result_nats)[2]:tail(colnames(result_nats),2)[1]) %>% 
  mutate(key = as.Date(key),
         group = "all")

#repeating for directors only

#mdl df of directors + section
  mdl_df2 <- df %>% 
  filter(fname == "Director" | fname == "Chief of Section") %>% 
  select(pname, fname_code,begin_date, end_date) %>% 
  mutate(begin_date = as.Date(begin_date),
         end_date = as.Date(end_date))

if(nrow(mdl_df2) == 0){
  print("no directors")}


result2 <- setDT(mdl_df2)[
  .(mseq = seq(as.Date("1919-01-01"), as.Date("1948-12-30"), by = interval)), 
  on = .(begin_date <= mseq, end_date >= mseq), nomatch = 0L, allow.cartesian = TRUE][
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]


result_nats2 <- left_join(result2, select(df, pname, nationality)) %>% 
  filter(!duplicated(.))

result_nats_wo_pname2 <- result_nats2[,-1]
 


nation_workers2 <- result_nats_wo_pname2 %>% 
  group_by(nationality) %>% 
  summarise_all(function(x) sum(x != ""))

long_df2 <- gather(nation_workers2, key, value, colnames(result_nats2)[2]:tail(colnames(result_nats2),2)[1]) %>%
  mutate(key = as.Date(key),
         group = "directors")  

long_df3 = rbind(long_df2,long_df)

#long_df3 %>% 
#  filter(value > minimum_worker) %>% 
#  ggplot(aes(x = key, y = value, fill = nationality, color = nationality)) +
#  geom_col() +
#  scale_x_date(date_breaks = "2 year", date_labels = "%Y") +
#  scale_y_continuous(limits = c(0,max_y),breaks = seq(0,max_y,2))  +
#  labs(x = x_axis, y =y_axis, titles = paste("Nationalities of the", title1))+
#  facet_grid(group~.)-> plot

long_df3 %>% 
  filter(value > minimum_worker) %>% 
  mutate(group = as.factor(group))-> plotdf

plotdf %>%   
ggplot(aes(x = key, y = value, fill = nationality, color = nationality)) +
  facet_grid(group~.)+
  geom_col(data = filter(plotdf, group == "all")) +
  geom_line(data = filter(plotdf, group == "directors")) +
  scale_x_date(date_breaks = "2 year", date_labels = "%Y") +
  scale_y_continuous(limits = c(0,max_y),breaks = seq(0,max_y,2))  +
  labs(x = x_axis, y =y_axis, titles = paste("Nationalities of the", title1))-> plot


return(plot)
}

```

```{r}
#plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[1])

#employment3(plot, title1 = levels(large_section_worker$oname)[1], max_y = 10)
```
```{r}
#plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[2])

#employment3(plot, title1 = levels(large_section_worker$oname)[2], max_y = 8)
```
```{r}
#plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[3])

#employment3(plot, title1 = levels(large_section_worker$oname)[3], max_y = 15)
```
No directors

```{r}
#plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[4])

#employment3(plot, title1 = levels(large_section_worker$oname)[4], max_y = 30)
```
```{r}
#plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[5])

#employment3(plot, title1 = levels(large_section_worker$oname)[5], max_y = 25)
```
```{r}
#plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[6])

#employment3(plot, title1 = levels(large_section_worker$oname)[6], max_y = 30)
```
```{r}
#plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[7])

#employment3(plot, title1 = levels(large_section_worker$oname)[7], max_y = 15)
```
No directors

```{r}
#plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[8])

#employment3(plot, title1 = levels(large_section_worker$oname)[8], max_y = 12)
```
# ```{r}
# plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[9])
# 
# employment3(plot, title1 = levels(large_section_worker$oname)[9], max_y = 6)
# ```
# ```{r}
# plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[10])
# 
# employment3(plot, title1 = levels(large_section_worker$oname)[10], max_y = 12)
# ```
# 
# 
# ```{r}
# plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[11])
# 
# employment3(plot, title1 = levels(large_section_worker$oname)[11], max_y = 15)
# ```
# ```{r}
# #plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[12])
# 
# #employment3(plot, title1 = levels(large_section_worker$oname)[12], max_y = 15)
# ```
# no directors
# ```{r}
# plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[13])
# 
# employment3(plot, title1 = levels(large_section_worker$oname)[13], max_y = 15)
# ```
# 
# 
# 
# 
# 
# ```{r}
# employment4 <- function(df, interval = "1 year", y_axis = "# of higher officials", x_axis = "Year", title1 = "LoN Workers", minimum_worker = 0, max_y = 50) {
#   
#   
# #mdl df without directors and chiefs of sections
# mdl_df <- df %>% 
#   filter(fname != "Director" & fname != "Chief of Section") %>% 
#   select(pname, fname_code,begin_date, end_date) %>% 
#   mutate(begin_date = as.Date(begin_date),
#          end_date = as.Date(end_date))
# 
# 
# 
# result <- setDT(mdl_df)[
#   .(mseq = seq(as.Date("1919-01-01"), as.Date("1948-12-30"), by = interval)), 
#   on = .(begin_date <= mseq, end_date >= mseq), nomatch = 0L, allow.cartesian = TRUE][
#     , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]
# 
# 
# result_nats <- left_join(result, select(df, pname, nationality)) %>% 
#   filter(!duplicated(.))
# 
# result_nats_wo_pname <- result_nats[,-1]
#  
# 
# 
# nation_workers <- result_nats_wo_pname %>% 
#   group_by(nationality) %>% 
#   summarise_all(function(x) sum(x != ""))
# 
# long_df <- gather(nation_workers, key, value, colnames(result_nats)[2]:tail(colnames(result_nats),2)[1]) %>% 
#   mutate(key = as.Date(key),
#          group = "all")
# 
# #repeating for directors only
# 
# #mdl df of directors + section
#   mdl_df2 <- df %>% 
#   filter(fname == "Director" | fname == "Chief of Section") %>% 
#   select(pname, fname_code,begin_date, end_date) %>% 
#   mutate(begin_date = as.Date(begin_date),
#          end_date = as.Date(end_date))
# 
# if(nrow(mdl_df2) == 0){
#   print("no directors")}
# 
# 
# result2 <- setDT(mdl_df2)[
#   .(mseq = seq(as.Date("1919-01-01"), as.Date("1948-12-30"), by = interval)), 
#   on = .(begin_date <= mseq, end_date >= mseq), nomatch = 0L, allow.cartesian = TRUE][
#     , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]
# 
# 
# result_nats2 <- left_join(result2, select(df, pname, nationality)) %>% 
#   filter(!duplicated(.))
# 
# result_nats_wo_pname2 <- result_nats2[,-1]
#  
# 
# 
# nation_workers2 <- result_nats_wo_pname2 %>% 
#   group_by(nationality) %>% 
#   summarise_all(function(x) sum(x != ""))
# 
# long_df2 <- gather(nation_workers2, key, value, colnames(result_nats2)[2]:tail(colnames(result_nats2),2)[1]) %>%
#   mutate(key = as.Date(key),
#          group = "directors")  
# 
# long_df3 = rbind(long_df2,long_df)
# 
# long_df3 %>% 
#   filter(value > minimum_worker) %>% 
#   ggplot(aes(x = key, y = value, fill = nationality, color = nationality)) +
#   geom_col() +
#   scale_x_date(date_breaks = "2 year", date_labels = "%Y") +
#   scale_y_continuous(limits = c(0,max_y),breaks = seq(0,max_y,2))  +
#   labs(x = x_axis, y =y_axis, titles = paste("Nationalities of the", title1))+
#   facet_grid(group~., scales = "free_y")-> plot
# 
# #long_df3 %>% 
# #  filter(value > minimum_worker) %>% 
# #  mutate(group = as.factor(group))-> plotdf
# 
# #plotdf %>%   
# #ggplot(aes(x = key, y = value, fill = nationality, color = nationality)) +
# #  facet_grid(group~.)+
# #  geom_col(data = filter(plotdf, group == "all")) +
# #  geom_line(data = filter(plotdf, group == "directors")) +
# #  scale_x_date(date_breaks = "2 year", date_labels = "%Y") +
# #  scale_y_continuous(limits = c(0,max_y),breaks = seq(0,max_y,2))  +
# #  labs(x = x_axis, y =y_axis, titles = paste("Nationalities of the", title1))-> plot
# 
# 
# return(plot)
# }
# 
# ```
# 
# 
# 
# ```{r}
# plot <- filter(large_section_worker,oname == levels(large_section_worker$oname)[10])
# 
# employment3(plot, title1 = levels(large_section_worker$oname)[10], max_y = 12)
# ```
# 
# 
# ```{r}
# 
# employment4(plot, title1 = levels(large_section_worker$oname)[10], max_y = 12)
```

