---
title: "Entrance, duration of contracts, accumulated experience"
author: "Adam Finnemann"
date: "October 19, 2017"
---
  
```{r setup}

library(pacman)
p_load("strmingr","ggplot2","ggExtra","lmerTest","tidyverse", "zoo","lubridate", "data.table")

setwd("~/Historie projekt/historie project/LONSEA_DB/fall17/yearly_length_contract_karen")

da <- read.csv(list.files(pattern = "contract_"))
```

## Question: For each year, how long does a person stay in the section?


First calculation: Subtracting end year of contract from beginning year. Take the average of this measure for each year and plot it per year.
Here it's assumed that all contracts start and end on the first 1. januar. In other words, only information about year differences is used.
```{r}

#why mutate no work??
da$begin_date <- as.Date(as.character(da$begin_date))         
da$end_date <- as.Date(as.character(da$end_date))         


da <-da  %>% 
  mutate(duration = end_date - begin_date)

da$begin_date <- as.factor(da$begin_date)
da$duration <- as.numeric(da$duration)
contract_length_per_year <- da %>% 
  group_by(begin_date) %>% 
  summarise(mean_length = mean(duration))


contract_length_per_year$begin_date <- as.Date(contract_length_per_year$begin_date)

contract_length_per_year %>% 
  ggplot(aes(begin_date,mean_length, color = mean_length)) +
  geom_point() +
  geom_smooth(se = F) +
  labs(x = "Year", y ="Days of contract", titles = "Average length of contract in years")+
  scale_x_date(date_breaks = "3 year", date_labels = "%Y")+
  scale_y_continuous(breaks = c(365, 365*2, 365*3, 365*4, 365*5, 365*6),labels = c("1 year", "2 years","3 years","4 years","5 years","6 years") )


```

```{r}
#employment interval function
employment <- function(df, interval = "1 year"){
  
mdl_df <- df %>% 
  select(pname, fname_code,begin_date, end_date) %>% 
  mutate(begin_date = as.Date(begin_date),
         end_date = as.Date(end_date))



result <- setDT(mdl_df)[
  .(mseq = seq(as.Date("1919-01-01"), as.Date("1948-12-30"), by = interval)), 
  on = .(begin_date <= mseq, end_date >= mseq), nomatch = 0L, allow.cartesian = TRUE][
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]
}

res <-employment(da) 
```


For each person, two measures are made: Number of years before they were employed, and the number of consecutive years their first employment period lasted. If a new contract starts the same year as the old one expires it's counted as consecutive. In other words, the second contract has to start in a different year than the first one expires. This means that up to 11 month long breaks can be counted as consecutive periods. 

Finally, for each year the average employment period of first time workers is calculated and visualized.

```{r}

wo_pname = res[,-1]
results <- matrix(NA, nrow = nrow(wo_pname), 2)

for (i in 1:nrow(wo_pname)) {
  count = 1
  blank = 0
  non_blank = 0
  new_blank = 0
  #while cells are blank add 1 to blank and counter
  while(wo_pname[i,count, with =F] =="") {
      blank = blank + 1
      count = count + 1
  }
    #if no new blanks and the current cell isn't empty
    while(wo_pname[i,count, with = F] != ""){
      non_blank = non_blank + 1
      count = count + 1
    }
  results[i,] <- c(blank, non_blank)
  }

```

```{r}
colnames(results) <- c("blanks","non_blank")

df <- results %>% 
  as.data.frame() %>% 
  mutate(pname = res$pname,
         begin_year = blanks + 1919,
         end_year = 1919 + blanks + non_blank,
         duration = end_year - begin_year) 

avg_len <- df %>% 
  group_by(begin_year) %>% 
  summarise(mean_len = mean(duration))
 
avg_len %>% 
  ggplot(aes(begin_year, mean_len, color = mean_len)) +
  geom_point()+
  geom_line()+
  labs(x = "Year", y ="Years of contract", titles = "Average length of first employment interval")+
  scale_x_continuous(breaks = seq(1919,1948,3))



```



Subsetting scandinavian people and repeating plot

```{r}
summary(da$nationality)
scandi <- da %>% 
  filter(nationality %in% c("Dane","Swedish","Norwegian"))

```

105 contract belonging to Scandinavians are found
```{r}
scandi_res <- employment(scandi)
wo_pname_scandi = scandi_res[,-1]
scandi_results <- matrix(NA, nrow = nrow(wo_pname_scandi), 2)

for (i in 1:nrow(wo_pname_scandi)) {
  count = 1
  blank = 0
  non_blank = 0
  new_blank = 0
  #while cells are blank add 1 to blank and counter
  while(wo_pname_scandi[i,count, with =F] =="") {
      blank = blank + 1
      count = count + 1
      
  }
    #if no new blanks and the current cell isn't empty
    while((wo_pname_scandi[i,count, with = F] != "") & count < ncol(wo_pname_scandi)-1){
      non_blank = non_blank + 1
      count = count + 1
        }
  
  scandi_results[i,] <- c(blank, non_blank)
}

```

```{r}
colnames(scandi_results) <- c("blanks","non_blank")

df <- scandi_results %>% 
  as.data.frame() %>% 
  mutate(pname = scandi_res$pname,
         begin_year = blanks + 1919,
         end_year = 1919 + blanks + non_blank,
         duration = end_year - begin_year) 

avg_len <- df %>% 
  group_by(begin_year) %>% 
  summarise(mean_len = mean(duration))
 
avg_len %>% 
  ggplot(aes(begin_year, mean_len, color = mean_len)) +
  geom_point()+
  geom_line()+
  labs(x = "Year", y ="Years of contract", titles = "Average length of first employment interval")+
  scale_x_continuous(breaks = seq(1919,1948,3))+
  scale_y_continuous(breaks = seq(1,12,2))
  
```

Visualizing number of first time contracts per year for Scandinavians
```{r}
df %>% 
  group_by(begin_year) %>% 
  tally() %>% 
  ggplot(aes(begin_year, n, fill = n)) +
  geom_col() +
  labs(x = "Year", y ="Nr. of contract", titles = "Number of first time contracts per year for Scandinavians")+
  scale_x_continuous(breaks = seq(1919,1948,3))+
  scale_y_continuous(breaks = seq(1,12,2))



```

Further subset, including only Scandinavians in Section and director

```{r}

top_scandi <- scandi %>% 
  filter(str_detect(scandi$fname, "Section") | str_detect(scandi$fname, "Director"),
         fname != "Secretary of Section")
unique(droplevels(top_scandi$pname))
```



This includes 24 contracts from 19 different people

```{r}

scandi_res <- employment(top_scandi)
```


```{r}
p <- top_scandi[which(!top_scandi$pname %in% scandi_res$pname),]
p
```

One contract is removed in the analysis: reason: begin_on_year is later than his end_on_year.



```{r}
wo_pname_scandi = scandi_res[,-1]
scandi_results <- matrix(NA, nrow = nrow(wo_pname_scandi), 2)

for (i in 1:nrow(wo_pname_scandi)) {
  count = 1
  blank = 0
  non_blank = 0
  new_blank = 0
  #while cells are blank add 1 to blank and counter
  while(wo_pname_scandi[i,count, with =F] =="") {
      blank = blank + 1
      count = count + 1
      
  }
    #if no new blanks and the current cell isn't empty
    while((wo_pname_scandi[i,count, with = F] != "") & count < ncol(wo_pname_scandi)-1){
      non_blank = non_blank + 1
      count = count + 1
        }
  
  scandi_results[i,] <- c(blank, non_blank)
}
colnames(scandi_results) <- c("blanks","non_blank")

df <- scandi_results %>% 
  as.data.frame() %>% 
  mutate(pname = scandi_res$pname,
         begin_year = blanks + 1919,
         end_year = 1919 + blanks + non_blank,
         duration = end_year - begin_year) 

avg_len <- df %>% 
  group_by(begin_year) %>% 
  summarise(mean_len = mean(duration))
 
avg_len %>% 
  ggplot(aes(begin_year, mean_len, fill = mean_len)) +
  geom_col() +
  labs(x = "Year", y ="Years of contract", titles = "Average length of first employment interval Scandis in First Division+Director")+
  scale_x_continuous(breaks = seq(1919,1948,3))+
  scale_y_continuous(breaks = seq(1,15,2))


```

Visualization number of contracts per year
```{r}
df %>% 
  group_by(begin_year) %>% 
  tally() %>% 
  ggplot(aes(begin_year, n, fill = n)) +
  geom_col() +
  labs(x = "Year", y ="Nr. of contract", titles = "Number of first time contracts per year for Scandinavians")+
  scale_x_continuous(breaks = seq(1919,1948,3))+
  scale_y_continuous(breaks = seq(1,12,2))


```


# New question: How many Scandinavians were there in section/directors over time:



```{r}


mdl_df <- top_scandi %>% 
  select(pname, fname_code,begin_date, end_date) %>% 
  mutate(begin_date = as.Date(begin_date),
         end_date = as.Date(end_date))



result <- setDT(mdl_df)[
  .(mseq = seq(as.Date("1919-01-01"), as.Date("1948-12-30"), by = "1 year")), 
  on = .(begin_date <= mseq, end_date >= mseq), nomatch = 0L, allow.cartesian = TRUE][
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]

scandi_workers <- result%>% 
  summarise_all(function(x) sum(x != ""))

long_df <- gather(scandi_workers, key, value, `1919-01-01`:`1946-01-01`) %>% 
  mutate(key = as.Date(key)) 
  

str(long_df)


 long_df %>% 
  ggplot(aes(x = key, y = value, fill = value)) +
  geom_col() +
  scale_x_date(date_breaks = "3 year", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(0,12,2))+
  labs(x = "Year", y ="Scandinavuans", titles = "Distribution of Scandinavians in section/directors")
  
```

Years with more than 7 Scandinavians in Section/director
```{r}
long_df %>% 
  filter(value > 7) %>% 
  ggplot(aes(x = key, y = value, fill = value)) +
  geom_col() +
  scale_x_date(date_breaks = "3 year", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(0,12,2))+
  labs(x = "Year", y ="Scandinavuans", titles = "Distribution of Scandinavians in section/directors")
```


## New question: What is the average years of employment (in total) per worker.
Decisions made: all years where a worked was present in LoN is counted (across breaks). Years are counted inclusively, so an employment period from 21 to 46 will give a total of 26 years on LoN.


defining function:

```{r}
employment_distribution <- function(df, xseq = seq(0,30,5),yseq = seq(0,2000, 250), group = "people"){ 
result <- employment(df)

contract_length <- matrix(nrow = (nrow(result)), ncol = 1)

result <- as.data.frame(result)

names <- as.character(result[,1])

#removing pname column 
contracts<- sapply(result[,-1],function(x) x != "") %>% 
  rowSums() %>% 
  as.data.frame() %>% 
  rename(contract_length = ".") %>% 
  mutate(names = as.factor(names))


contracts %>% 
  ggplot(aes(contract_length, color = contract_length)) +
  geom_histogram(binwidth = 1, aes(fill = ..count..)) +
  scale_fill_gradient("count", low="orange", high="purple") +
  labs(x = "Work periods in years", y = "Number of people", title = paste("Distribution of work periods in LoN for",group)) +
  scale_x_continuous(breaks = xseq)+
  scale_y_continuous(breaks = yseq)
}
```


```{r}

employment_distribution(da, group = "everyone")

```

repeating analysis for all scandinavians

```{r}
employment_distribution(scandi,xseq = seq(0,30,1), yseq = seq(0,1500,10), group ="Scandinavians")
```

Repeating analysis for scandinavians in First division

```{r}
employment_distribution(top_scandi, yseq = seq(0,3,1), group = "Scandinavians in First Division")

```

Same analysis for full section and each section + directors:

```{r}
section_da <- da%>%
filter(str_detect(da$fname, "Section") | str_detect(da$fname, "Director"),
         fname != "Secretary of Section")

employment_distribution(section_da, yseq = seq(0,100,5), group = "Section and directors")

```

Further analysis of each section is carried out on section with more than 10 total contracts. These are roughly:
health, disarmament, mandates, legal, communications and transit, information, economic and financial section (which goes together with the economic relations section and the financial & economic intelligence service), intellectual cooperation and international bureaux section, minorities (which go together with Administrative and Minorities), the social questions and opium traffic, and the political section

First the three economic sections are united to 1. Same for "Minorities" and "Admin. and Minotories".

```{r}

oname_correct <- section_da %>% 
  mutate(oname = str_replace_all(oname, "Financial Section & Economic Intelligence Service","Economic and Financial Section"),
        oname = str_replace_all(oname, "Economic Relations Section","Economic and Financial Section")
         ) %>% 
  mutate(oname = as.factor(oname),
         oname = recode(oname, "Minorities Section" = "Administrative and Minorities Section"))


large_sections <- oname_correct %>% 
  group_by(oname) %>% 
  filter(n() >10) %>% 
  ungroup() %>% 
  mutate(oname = droplevels(oname))
summary(large_sections$oname)
```
Keeping only large sections reduces number of contracts in analysis from 422 to 354.

```{r}


employment_distribution(filter(large_sections, oname == levels(oname)[1]),xseq = seq(0,30,1), yseq = seq(0,100,1), group = levels(large_sections$oname)[1])


```

```{r}
employment_distribution(filter(large_sections, oname == levels(oname)[2]),xseq = seq(0,30,1), yseq = seq(0,100,1), group = levels(large_sections$oname)[2])


```

```{r}
employment_distribution(filter(large_sections, oname == levels(oname)[3]),xseq = seq(0,30,1), yseq = seq(0,100,1), group = levels(large_sections$oname)[3])


```

```{r}
employment_distribution(filter(large_sections, oname == levels(oname)[4]),xseq = seq(0,30,1), yseq = seq(0,100,1), group = levels(large_sections$oname)[4])

```

```{r}
employment_distribution(filter(large_sections, oname == levels(oname)[5]),xseq = seq(0,30,1), yseq = seq(0,100,1), group = levels(large_sections$oname)[5])


```

```{r}
employment_distribution(filter(large_sections, oname == levels(oname)[6]),xseq = seq(0,30,1), yseq = seq(0,100,1), group = levels(large_sections$oname)[6])


```

```{r}
employment_distribution(filter(large_sections, oname == levels(oname)[7]),xseq = seq(0,30,1), yseq = seq(0,100,1), group = levels(large_sections$oname)[7])


```

```{r}
employment_distribution(filter(large_sections, oname == levels(oname)[8]),xseq = seq(0,30,1), yseq = seq(0,100,1), group = levels(large_sections$oname)[8])

```

```{r}
employment_distribution(filter(large_sections, oname == levels(oname)[9]),xseq = seq(0,30,1), yseq = seq(0,100,1), group = levels(large_sections$oname)[9])

```

```{r}
employment_distribution(filter(large_sections, oname == levels(oname)[10]),xseq = seq(0,30,1), yseq = seq(0,100,1), group = levels(large_sections$oname)[10])


```

```{r}
employment_distribution(filter(large_sections, oname == levels(oname)[11]),xseq = seq(0,30,1), yseq = seq(0,100,1), group = levels(large_sections$oname)[11])


```

```{r}
employment_distribution(filter(large_sections, oname == levels(oname)[12]),xseq = seq(0,30,1), yseq = seq(0,100,1), group = levels(large_sections$oname)[12])

```


Continuing analysis for regions: Scandinavia, South Americans, France, Swiss, Britain.
(Afterwards a seperate analysis is made for european countries)
```{r}
five_nat.df <- da
five_nat.df$nationality <-str_replace_all(five_nat.df$nationality,"Dane", "Scandinavian")
five_nat.df$nationality <-str_replace_all(five_nat.df$nationality,"Swedish", "Scandinavian")
five_nat.df$nationality <-str_replace_all(five_nat.df$nationality,"Norwegian", "Scandinavian")
five_nat.df$nationality <-str_replace_all(five_nat.df$nationality,"Brazilian\t", "South American")
five_nat.df$nationality <-str_replace_all(five_nat.df$nationality,"Uruguayan", "South American")
five_nat.df$nationality <-str_replace_all(five_nat.df$nationality,"Peruvian", "South American")
five_nat.df$nationality <-str_replace_all(five_nat.df$nationality,"Argentinian", "South American")
five_nat.df$nationality <-str_replace_all(five_nat.df$nationality,"Chilean", "South American")
five_nat.df$nationality <-str_replace_all(five_nat.df$nationality,"Venezuelan\t", "South American")
five_nat.df$nationality <-str_replace_all(five_nat.df$nationality,"Paraguayan", "South American")
five_nat.df$nationality <-str_replace_all(five_nat.df$nationality,"Ecuadorian", "South American")
five_nat.df$nationality <-str_replace_all(five_nat.df$nationality,"Bolivian", "South American")
five_nat.df$nationality <-str_replace_all(five_nat.df$nationality,"English", "British")         


five_nats <- five_nat.df %>% 
  filter(nationality == "British"|nationality == "South American"| nationality == "Scandinavian"| nationality == "Swiss"| nationality == "French") %>% 
  mutate(nationality = as.factor(nationality))


```


For all 5 nationalities
```{r}
employment_distribution(five_nats,xseq = seq(0,30,1), yseq = seq(0,1500,100), group = levels(large_sections$oname)[12])


```
```{r}

employment_distribution(filter(five_nats, nationality == levels(nationality)[1]),xseq = seq(0,30,1), yseq = seq(0,1500,50), group = levels(five_nats$nationality)[1])

```
```{r}
employment_distribution(filter(five_nats, nationality == levels(nationality)[2]),xseq = seq(0,30,1), yseq = seq(0,1500,50), group = levels(five_nats$nationality)[2])
```

```{r}
employment_distribution(filter(five_nats, nationality == levels(nationality)[3]),xseq = seq(0,30,1), yseq = seq(0,1500,10), group = levels(five_nats$nationality)[3])
```
```{r}
employment_distribution(filter(five_nats, nationality == levels(nationality)[4]),xseq = seq(0,30,1), yseq = seq(0,1500,1), group = levels(five_nats$nationality)[4])
```

```{r}
employment_distribution(filter(five_nats, nationality == levels(nationality)[5]),xseq = seq(0,30,1), yseq = seq(0,1500,50), group = levels(five_nats$nationality)[5])
```


##New analysis: accumulated experience over time
Experience is interpret as the accumulated number of previous years workers have been in the league. 
This is plottet against the number of workers per year (this can ofc be changed).


```{r}
#turn into function for later use
#employment_distribution <- function(df, yseq = seq(0,2000, 250), group = "people"){ 

  result <- employment(da)
  
  contract_length <- matrix(nrow = (nrow(result)), ncol = 1)
  
  result <- as.data.frame(result)
  
  names <- as.character(result[,1])

  wo_pname <- result[,-1]
  
  
  
  #starting a second year
  accumulated_experience <- matrix(NA, nrow = ncol(wo_pname))
  
  for (i in 2:ncol(wo_pname)){
    current_workers <- which(wo_pname[,i] != "")
    
    years_of_experience <- wo_pname[current_workers,1:(i-1)]%>% 
      as.data.frame() %>% 
  summarise_all(function(x) sum(x != "")) %>% sum
    
    accumulated_experience[i] = years_of_experience
    
  }
    
  worker <- wo_pname%>% 
  summarise_all(function(x) sum(x != "")) %>%
    t %>% 
    as.data.frame()
                  
  
  accumulated_experience <- accumulated_experience %>% 
    as.data.frame() %>% 
    mutate(year = colnames(wo_pname),
           year = as.Date(year),
           nr_worker = worker$V1)
  accumulated_experience[1,1] = 0
          
accumulated_experience$nr_worker <- as.numeric(accumulated_experience$nr_worker)  
  
accumulated_experience %>% 
    ggplot(aes(x=year)) +
    geom_line(aes(y = V1), color = "blue")+
    geom_line(aes(y = nr_worker), color = "red") +
    scale_x_date(date_breaks = "2 years", date_labels = "%Y")+
    labs(x = "Workers and accum. exp.", y = "Year", title = "Number of workers (red) and accumulated experience (blue)")

```


