---
title: "Entrance and duration of contracts"
author: "Adam Finnemann"
date: "September 24, 2017"
---
  
```{r setup, include=FALSE}

library(pacman)
p_load("stringr","ggplot2","ggExtra","lmerTest","tidyverse", "zoo","lubridate", "data.table")

setwd("~/Historie projekt/historie project/LONSEA_DB/fall17/yearly_length_contract_karen")

da <- read.csv(list.files(pattern = "contract_"))
```

Question: For each year, how long does a person stay in the section?


First calculation: Subtracting end year of contract from beginning year. Take the average of this measure for each year and plot it per year.
Here it's assumed that all contracts start and end on the first 1. januar. In other words, only information about year differences is used.
```{r}

#why mutate no work??
da$begin_date <- as.Date(as.character(da$begin_date))         
da$end_date <- as.Date(as.character(da$end_date))         


da <-da  %>% 
  mutate(duration = end_date - begin_date)

da$begin_date <- as.factor(da$begin_date)
da$duration <- as.numeric(da$duration)
contract_length_per_year <- da %>% 
  group_by(begin_date) %>% 
  summarise(mean_length = mean(duration))


contract_length_per_year$begin_date <- as.Date(contract_length_per_year$begin_date)

contract_length_per_year %>% 
  ggplot(aes(begin_date,mean_length, color = mean_length)) +
  geom_point() +
  geom_smooth(se = F) +
  labs(x = "Year", y ="Days of contract", titles = "Average length of contract in years")+
  scale_x_date(date_breaks = "3 year", date_labels = "%Y")+
  scale_y_continuous(breaks = c(365, 365*2, 365*3, 365*4, 365*5, 365*6),labels = c("1 year", "2 years","3 years","4 years","5 years","6 years") )


```

```{r}
#employment interval function
employment <- function(df, interval = "1 year"){
  
mdl_df <- df %>% 
  select(pname, fname_code,begin_date, end_date) %>% 
  mutate(begin_date = as.Date(begin_date),
         end_date = as.Date(end_date))



result <- setDT(mdl_df)[
  .(mseq = seq(as.Date("1919-01-01"), as.Date("1948-12-30"), by = interval)), 
  on = .(begin_date <= mseq, end_date >= mseq), nomatch = 0L, allow.cartesian = TRUE][
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]
}

res <-employment(da) 
```


For each person, two measures are made: Number of years before they were employed, and the number of consecutive years their first employment period lasted. If a new contract starts the same year as the old one expires it's counted as consecutive. In other words, the second contract has to start in a different year than the first one expires. This means that up to 11 month long breaks can be counted as consecutive periods. 

Finally, for each year the average employment period of first time workers is calculated and visualized.

```{r}

wo_pname = res[,-1]
results <- matrix(NA, nrow = nrow(wo_pname), 2)

for (i in 1:nrow(wo_pname)) {
  count = 1
  blank = 0
  non_blank = 0
  new_blank = 0
  #while cells are blank add 1 to blank and counter
  while(wo_pname[i,count, with =F] =="") {
      blank = blank + 1
      count = count + 1
  }
    #if no new blanks and the current cell isn't empty
    while(wo_pname[i,count, with = F] != ""){
      non_blank = non_blank + 1
      count = count + 1
    }
  results[i,] <- c(blank, non_blank)
  }

```

```{r}
colnames(results) <- c("blanks","non_blank")

df <- results %>% 
  as.data.frame() %>% 
  mutate(pname = res$pname,
         begin_year = blanks + 1919,
         end_year = 1919 + blanks + non_blank,
         duration = end_year - begin_year) 

avg_len <- df %>% 
  group_by(begin_year) %>% 
  summarise(mean_len = mean(duration))
 
avg_len %>% 
  ggplot(aes(begin_year, mean_len, color = mean_len)) +
  geom_point()+
  geom_line()+
  labs(x = "Year", y ="Years of contract", titles = "Average length of first employment interval")+
  scale_x_continuous(breaks = seq(1919,1948,3))



```



Subsetting scandinavian people and repeating plot

```{r}
summary(da$nationality)
scandi <- da %>% 
  filter(nationality %in% c("Dane","Swedish","Norwegian"))

```

105 contract belonging to Scandinavians are found
```{r}
scandi_res <- employment(scandi)
wo_pname_scandi = scandi_res[,-1]
scandi_results <- matrix(NA, nrow = nrow(wo_pname_scandi), 2)

for (i in 1:nrow(wo_pname_scandi)) {
  count = 1
  blank = 0
  non_blank = 0
  new_blank = 0
  #while cells are blank add 1 to blank and counter
  while(wo_pname_scandi[i,count, with =F] =="") {
      blank = blank + 1
      count = count + 1
      
  }
    #if no new blanks and the current cell isn't empty
    while((wo_pname_scandi[i,count, with = F] != "") & count < ncol(wo_pname_scandi)-1){
      non_blank = non_blank + 1
      count = count + 1
        }
  
  scandi_results[i,] <- c(blank, non_blank)
}

```

```{r}
colnames(scandi_results) <- c("blanks","non_blank")

df <- scandi_results %>% 
  as.data.frame() %>% 
  mutate(pname = scandi_res$pname,
         begin_year = blanks + 1919,
         end_year = 1919 + blanks + non_blank,
         duration = end_year - begin_year) 

avg_len <- df %>% 
  group_by(begin_year) %>% 
  summarise(mean_len = mean(duration))
 
avg_len %>% 
  ggplot(aes(begin_year, mean_len, color = mean_len)) +
  geom_point()+
  geom_line()+
  labs(x = "Year", y ="Years of contract", titles = "Average length of first employment interval")+
  scale_x_continuous(breaks = seq(1919,1948,3))+
  scale_y_continuous(breaks = seq(1,12,2))
  
```

Visualizing number of first time contracts per year for Scandinavians
```{r}
df %>% 
  group_by(begin_year) %>% 
  tally() %>% 
  ggplot(aes(begin_year, n, fill = n)) +
  geom_col() +
  labs(x = "Year", y ="Nr. of contract", titles = "Number of first time contracts per year for Scandinavians")+
  scale_x_continuous(breaks = seq(1919,1948,3))+
  scale_y_continuous(breaks = seq(1,12,2))



```

Further subset, including only Scandinavians in Section and director

```{r}

top_scandi <- scandi %>% 
  filter(str_detect(scandi$fname, "Section") | str_detect(scandi$fname, "Director"),
         fname != "Secretary of Section")
unique(droplevels(top_scandi$pname))
```



This includes 24 contracts from 19 different people

```{r}

scandi_res <- employment(top_scandi)
```


```{r}
p <- top_scandi[which(!top_scandi$pname %in% scandi_res$pname),]
p
```

One person is removed in the analysis: apparent reason, his begin_on_year is later than his end_on_year.



```{r}
wo_pname_scandi = scandi_res[,-1]
scandi_results <- matrix(NA, nrow = nrow(wo_pname_scandi), 2)

for (i in 1:nrow(wo_pname_scandi)) {
  count = 1
  blank = 0
  non_blank = 0
  new_blank = 0
  #while cells are blank add 1 to blank and counter
  while(wo_pname_scandi[i,count, with =F] =="") {
      blank = blank + 1
      count = count + 1
      
  }
    #if no new blanks and the current cell isn't empty
    while((wo_pname_scandi[i,count, with = F] != "") & count < ncol(wo_pname_scandi)-1){
      non_blank = non_blank + 1
      count = count + 1
        }
  
  scandi_results[i,] <- c(blank, non_blank)
}
colnames(scandi_results) <- c("blanks","non_blank")

df <- scandi_results %>% 
  as.data.frame() %>% 
  mutate(pname = scandi_res$pname,
         begin_year = blanks + 1919,
         end_year = 1919 + blanks + non_blank,
         duration = end_year - begin_year) 

avg_len <- df %>% 
  group_by(begin_year) %>% 
  summarise(mean_len = mean(duration))
 
avg_len %>% 
  ggplot(aes(begin_year, mean_len, fill = mean_len)) +
  geom_col() +
  labs(x = "Year", y ="Years of contract", titles = "Average length of first employment interval Scandis in First Division+Director")+
  scale_x_continuous(breaks = seq(1919,1948,3))+
  scale_y_continuous(breaks = seq(1,15,2))


```

Visualization number of contracts per year
```{r}
df %>% 
  group_by(begin_year) %>% 
  tally() %>% 
  ggplot(aes(begin_year, n, fill = n)) +
  geom_col() +
  labs(x = "Year", y ="Nr. of contract", titles = "Number of first time contracts per year for Scandinavians")+
  scale_x_continuous(breaks = seq(1919,1948,3))+
  scale_y_continuous(breaks = seq(1,12,2))


```


New question: How many Scandinavians were there in section/directors over time:

```{r}


mdl_df <- top_scandi %>% 
  select(pname, fname_code,begin_date, end_date) %>% 
  mutate(begin_date = as.Date(begin_date),
         end_date = as.Date(end_date))



result <- setDT(mdl_df)[
  .(mseq = seq(as.Date("1919-01-01"), as.Date("1948-12-30"), by = "1 year")), 
  on = .(begin_date <= mseq, end_date >= mseq), nomatch = 0L, allow.cartesian = TRUE][
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]

scandi_workers <- result%>% 
  summarise_all(function(x) sum(x != ""))

long_df <- gather(nation_workers, key, value, `1919-01-01`:`1946-01-01`) %>% 
  mutate(key = as.Date(key)) 
  

str(long_df)


 long_df %>% 
  ggplot(aes(x = key, y = value, fill = value)) +
  geom_col() +
  scale_x_date(date_breaks = "3 year", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(0,12,2))+
  labs(x = "Year", y ="Scandinavuans", titles = "Distribution of Scandinavians in section/directors")
  
```

Years with more than 7 Scandinavians in Section/director
```{r}
long_df %>% 
  filter(value > 7) %>% 
  ggplot(aes(x = key, y = value, fill = value)) +
  geom_col() +
  scale_x_date(date_breaks = "3 year", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(0,12,2))+
  labs(x = "Year", y ="Scandinavuans", titles = "Distribution of Scandinavians in section/directors")
```


## New question: What is the average years of employment (in total) per worker.
Could be considered repeating analysis for monthly interval.

```{r}
result <- employment(da)

contract_length <- matrix(nrow = (nrow(result)), ncol = 1)

result <- as.data.frame(result)

names <- as.character(result[,1])

#removing pname column 
contracts<- sapply(result[,-1],function(x) x != "") %>% 
  rowSums() %>% 
  as.data.frame() %>% 
  rename(contract_length = ".") %>% 
  mutate(names = as.factor(names))


contracts %>% 
  ggplot(aes(contract_length, color = contract_length)) +
  geom_histogram( aes(fill = ..count..)) +
  scale_fill_gradient("count", low="orange", high="purple") +
  labs(x = "Work periods in years", y = "Number of people", title = "Distribution of work periods in LoN") +
  scale_x_continuous(breaks = seq(0,30,5))+
  scale_y_continuous(breaks = seq(0,2000, 250))

```

