```{r setup}

library(pacman)
p_load("strmingr","ggplot2","ggExtra","lmerTest","tidyverse", "zoo","lubridate", "data.table", "ggthemes")

setwd("~/Historie projekt/historie project/LONSEA_DB/spring18/proportion_of_scandis")

da <- read.csv(list.files(pattern = "contract_"))
```


Subsetting scandinavians with section, director, chief, expert in fname (excluding sectretary of sections).

```{r}
da$end_date = as.Date(da$end_date)

#da$end_date = da$end_date - 1


direc = da %>% 
  filter(str_detect(da$fname, "Director") | pname == "Dame Rachel Eleanor Crowdy") %>%  
  filter(pname != "L. Varlez" & fname != "Member of Section") %>%  #removing Varlez and Dame Crowdy's "member of section contract"
  droplevels()


direc$pname
```
Above is the list of director contracts included. There are 32 different people, and some with multiple contracts

overview of people with multiple contracts.
```{r}
direc[duplicated(direc$pname),]
```



```{r}

mdl_df <- direc %>% 
  select(pname, fname_code,begin_date, end_date) %>% 
  mutate(begin_date = as.Date(begin_date),
         end_date = as.Date(end_date))

result <- setDT(mdl_df)[
  .(mseq = seq(as.Date("1919-01-01"), as.Date("1948-12-30"), by = "1 year")), 
  on = .(begin_date <= mseq, end_date >= mseq), nomatch = 0L, allow.cartesian = TRUE][
    , dcast(unique(.SD), pname ~ end_date, toString, value.var = "fname_code")]
```

Checking if all directors are still in the analysis
```{r}
nlevels(direc$pname)

```
they are


```{r}
result_nats <- left_join(result, select(direc, pname, nationality)) %>% 
  filter(!duplicated(.))
```

#Nationality of directors over time

```{r}
result_nats_wo_pname <- result_nats[,-1]
 

nation_workers <- result_nats_wo_pname %>% 
  group_by(nationality) %>% 
  summarise_all(function(x) sum(x != ""))

long_df <- gather(nation_workers, key, value, `1919-01-01`:`1947-01-01`) %>% 
  mutate(key = as.Date(key)) 
  


#function for plotting

plot_section_workers <- function(df, minimum_worker = 5){
df %>% 
  filter(value > minimum_worker) %>% 
  ggplot(aes(x = key, y = value, fill = nationality, color = nationality)) +
  geom_col() +
  scale_x_date(date_breaks = "2 year", date_labels = "%Y") +
  labs(x = "Year", y ="Workers", titles = paste("Nations with more than", minimum_worker,"directors in Section"))
}



plot_section_workers(long_df, 2)

```

```{r}
plot_section_workers(long_df, 1)

```

```{r}
plot_section_workers(long_df, 0)

```


# Directors per section over time.


```{r}

result_oname <- left_join(result, select(direc, pname, oname)) %>% 
  filter(!duplicated(.))

result_oname_wo_pname <- result_oname[,-1]
 

oname_workers <- result_oname_wo_pname %>% 
  group_by(oname) %>% 
  summarise_all(function(x) sum(x != ""))

oname_df <- gather(oname_workers, key, value, `1919-01-01`:`1947-01-01`) %>% 
  mutate(key = as.Date(key)) 
  


#function for plotting

plot_section_workers <- function(df, minimum_worker = 5){
df %>% 
  filter(value > minimum_worker) %>% 
  ggplot(aes(x = key, y = value, fill = oname, color = oname)) +
  geom_col() +
  scale_x_date(date_breaks = "2 year", date_labels = "%Y") +
  labs(x = "Year", y ="Workers", titles = paste("Sections with more than", minimum_worker,"directors"))+
  scale_y_continuous(breaks =  1:8)
}



plot_section_workers(oname_df, 2)

```

```{r}
plot_section_workers(oname_df, 1)
```


```{r}
plot_section_workers(oname_df, 0)
```
Plot without legend

```{r}
plot_section_workers <- function(df, minimum_worker = 5){
df %>% 
  filter(value > minimum_worker) %>% 
  ggplot(aes(x = key, y = value, fill = oname, color = oname)) +
  geom_col() +
  scale_x_date(date_breaks = "2 year", date_labels = "%Y") +
  labs(x = "Year", y ="Workers", titles = paste("Sections with more than", minimum_worker,"directors"))+
  scale_y_continuous(breaks =  1:8) +
  theme(legend.position="none")
}

plot_section_workers(oname_df, 0)
```

