

```{r}
library(pacman)
p_load("stringr","ggplot2","ggExtra","lmerTest","tidyverse", "zoo","lubridate", "data.table")

setwd("~/Historie projekt/historie project/LONSEA_DB/spring18/proportion_of_scandis")

da <- read.csv("contract_length_w_begin_year.csv")

higher_officials2 <- da %>% 
  filter(str_detect(fname, "Section")| #including "Section"
           str_detect(fname, "Director")| #Including Directors
           str_detect(fname, "Chief") | #Including Chief
           str_detect(fname, "Expert")|
           str_detect(fname, "Head of") |
           str_detect(fname, "Under Secretary General"),
         fname != "Secretary of Section",
         oname != "Treasury",
         oname != "Library",
         canonical_fname != "Second Division") %>% 
  #filter(canonical_fname != "First Division" & str_detect(da$fname, "Head") %>% 
  droplevels()
```

Higher officials defined as members, of sesctions ,directors, chiefs of section, experts, heads of section, under secretary generals. Excluded are secretaries, treasury and library. 
This amounts to 503 contracts.

##How many higher officials had contract start in 1919 or 1920

```{r}
higher_officials2 %>% 
  filter(begin_on_year == 1919 |  begin_on_year == 1920) %>% 
  group_by(begin_on_year) %>% 
  summarise(starts = n())
```

There are a total of 70 contracts spread over 1919 and 1920

###Per country how many contract starts in 1919 or 1920
```{r}
higher_officials2 %>% 
  filter(begin_on_year == 1919 |  begin_on_year == 1920) %>% 
  group_by( nationality) %>% 
  summarise(starts = n())
```

##Average age of higher officials starting in 1919 or 1920
This is calculated by subtracting born_on_year from begin_on_year.
18 out of 70 contracts are missing born_on_year and are excluded from the analysis.

```{r}
higher_officials2 %>% 
  filter(begin_on_year == 1919 |  begin_on_year == 1920) %>% 
  filter(!is.na(born_on_year)) %>% 
  summarise(mean_age = mean(  begin_on_year- born_on_year))
```


##Gender composition


```{r}
higher_officials2 %>% 
  filter(begin_on_year == 1919 |  begin_on_year == 1920) %>% 
  group_by(gender) %>% 
  tally()
```
There are 67 males and 3 woman
