---
title: "Exploring missing data"
author: "Adam Finnemann"
date: "September 24, 2017"
---
  
```{r setup, include=FALSE}

library(pacman)
p_load("stringr","ggplot2","ggExtra","lmerTest","tidyverse", "zoo","lubridate", "data.table")



setwd("~/Historie projekt/historie project/LONSEA_DB/fall17")
da_mis <- read.csv("missing_begin_on_year.csv")

```
There are a total of 5198 contract with missing beginning year of contract

```{r}
da_mis %>% group_by(nationality) %>% tally()


```
4816 of the contract are missing nationality as well
```{r}
da_mis %>% group_by(oname) %>% tally()

```


```{r}
GA_worker <- da_mis %>% 
  filter(str_detect(da_mis$fname, "General Assembly"))

#write.csv(GA_worker, "missing_data/General_Assemb_workers.csv")

non_GA_worker <- da_mis %>% 
  filter(!str_detect(da_mis$fname, "General Assembly"))
write.csv(non_GA_worker, "missing_data/non_General_Assemb_workers.csv")

```
5098 of the missing contracts are from the General Assembly.
Table of these are found in General_Assemb_worker.csv

813 contract are not from the General assembly
Table of these are found in non_General_Assemb_worker.csv

List of "important" missing contracts i.e. contracts from first division are in the folder first_div_missing_workers. Tis amounts to 139 contracts including directors, head of sections, deputy chiefs.
```{r}
missing_first_div <- filter(non_GA_worker, canonical_fname == "First Division")

write.csv(missing_first_div, "missing_data/first_div_missing_workers.csv")

```

